---
title: "INLA spde modeling of individual level Aedes mosquito exposure among Cambodian children"
output: pdf_document
header-includes:
  - \usepackage{float}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
classoption: landscape
params:
  rerun_data: FALSE
  near_river_cut_off: 300
  modis_lag: 32
  refit_fit: FALSE
  refit_vistit_fit: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, eval = FALSE, 
  fig.pos = 'H', fig.align = "center",
  message = FALSE, warning = FALSE
)
```


```{r libraries, eval = TRUE}
library(here)
library(readxl)
library(janitor)
library(zoo)
library(RANN)
library(viridis)
library(gridExtra)
library(knitr)
library(sf)
library(ggsn)
library(ggmap)
library(lattice)
library(magrittr)
library(knitr)
library(kableExtra)
library(INLAutils)
library(extrafont)
library(tidyverse)
library(INLA)

loadfonts(device = "win")
windowsFonts(Times = windowsFont("TT Times New Roman"))

source(here("analysis", "process-modis-data-function.R"))
```


```{r read-process-data}
if (!params$rerun_data) {
  
  aedes_red <- readRDS(file = here("data", "processed_aedes_data.rds"))
  
  aedes_red_ind <- aedes_red %>%
  filter(visit == "visit1") %>% 
  mutate(visit = droplevels(visit))
  
} else {
  
  ##### read-process-survey-data
  
  saliva_ELISA_log_shift <- 0.15
  
  sched_visit_names <- c(
    "VISIT 1 DENGUE INDEX",
    "VISIT 2  DENGUE INDEX",
    "VISIT 3 DENGUE INDEX",
    "VISIT 4 INDEX"
  )
  
  low_count_schools <- c( # schools with <= 5 study participants with saliva measurement
    "Amnor Antarak Cheat School",
    "Ampe Phnom",
    "Aphivodth", 
    "Christian School Khum Skus",
    "Kdey Amnor", 
    "Kindergarten Asian",
    "Kindergarten Kampuchea Asian",
    "Kindergarten Wattbor",
    "Kindergarten​ Salon",
    "Meatophoum School",
    "No Name",
    "Panha Bot School",
    "Phoumi Thmei",
    "Sinsisamuth"
  ) 
  
  
  aedes_survey_og <- read_excel(here("data", "pagodas_combined_data3.xlsx"))
  
  
  aedes_survey_cleaned <- aedes_survey_og %>% 
    clean_names() %>% 
    mutate(wet_season = ifelse(
      visit %in% c("VISIT 1 DENGUE INDEX", "VISIT 3 DENGUE INDEX"),
      yes = "yes",
      no = "no"
    )) %>% 
    mutate(visit_year = case_when(
      visit == "VISIT 1 DENGUE INDEX" ~ 0,
      visit %in% c("VISIT 2  DENGUE INDEX", "VISIT 3 DENGUE INDEX") ~ 1,
      visit == "VISIT 4 INDEX" ~ 2,
      TRUE ~ -99
    )) %>% 
    mutate(age = as.numeric(age)) %>% 
    mutate(age_cented3 = age - 3) %>%
    mutate(age_cented7 = age - 7) %>%
    mutate(age_cented = age - 6) %>%
    mutate(gender = factor(gender)) %>% 
    mutate(school_attended = str_to_title(school_attended)) %>% 
    mutate(specify_if_other = str_to_title(specify_if_other)) %>% 
    mutate(school_attended_all = ifelse(
      school_attended == "Other, Specify:",
      yes = specify_if_other,
      no = school_attended
    )) %>% 
    mutate(school_attended_all = factor(
      case_when(
        school_attended_all == "New Town" ~ "Kindergarten New Town",
        school_attended_all %in% c("Sin Si Sa Muth", "Sinsisamuth") ~ "Kindergarten Sin Si Sa Muth",
        school_attended_all == "Panha Bot" ~ "Panha Bot School",
        school_attended_all == "No Name" ~ "NA",
        TRUE ~ school_attended_all
      ))) %>% 
    mutate(school_attended_all = as.character(school_attended_all)) %>%
    mutate(in_school = factor(ifelse(
      school_attended_all != "Subject Not In School",
      yes = "yes",
      no = "no"
    ))) %>% 
    mutate(school_attended_red = factor(
      case_when(
        school_attended_all %in% low_count_schools ~ "other",
        TRUE ~ school_attended_all
      ),
      levels = c(
        "Subject Not In School",
        "Ang Seri",              
        "Anouvotta",             
        "Mroum Cheung",          
        "Mroum Tbaung",          
        "New Town",
        "Rkathom",
        "Santiphap",
        "Kindergarten Sin Si Sa Muth",
        "other"
      )
    )) %>% 
    select(-c("specify_if_other")) %>% 
    mutate(housing_type = factor(housing_type)) %>% 
    mutate(socioeconomic_class = factor(
      socioeconomic_class,
      levels = c("Very Poor", "Lower", "Middle", "Upper")
    )) %>% 
    mutate(visit_date = as.Date(visit_date)) %>% 
    mutate(sched_visit = ifelse(visit %in% sched_visit_names, yes = "yes", no = "no")) %>% 
    mutate(num_domestic_water_containers_in_home = as.numeric(num_domestic_water_containers_in_home)) %>% 
    mutate(num_toilets_in_home = as.numeric(num_toilets_in_home)) %>% 
    mutate(how_often_use_bed_net = factor(
      how_often_use_bed_net,
      levels = c(
        "Never", 
        "Rarely", 
        "Regularly/ Most of the time", 
        "All of the time"
      ),
      labels = c(
        "Never", 
        "Rarely", 
        "Most of the time", 
        "All of the time"
      )
    )) %>% 
    mutate(insecticide_spray = factor(insecticide_spray)) %>% 
    mutate(larvicide_applied_to_water = factor(larvicide_applied_to_water)) %>% 
    mutate(how_often_mosquito_coils_burned = factor(
      how_often_mosquito_coils_burned,
      levels = c(
        "Never", 
        "Rarely (about 1x/month)", 
        "Sometimes (about 1x/week)",
        "Often (about 3x/week)",
        "Daily"
      ),
      labels = c(
        "Never", 
        "~ 1x/month", 
        "~ 1x/week",
        "~ 3x/week",
        "Daily"
      )
    )) %>% 
    mutate(visit_date_abr = factor(as.yearmon(visit_date))) %>% 
    mutate(log_saliva_elisa = log(saliva_elisa_value + saliva_ELISA_log_shift)) 
  
  
  aedes_visit5 <- read_csv(here("data", "Saliva ELISA V1-6 INDEX.csv"), show_col_types = FALSE) %>% 
    select(study_id = ID, saliva_elisa_value = "Visit 5") %>% 
    mutate(saliva_elisa_value = as.numeric(ifelse(saliva_elisa_value == ".", yes = NA, no = saliva_elisa_value))) %>% 
    mutate(log_saliva_elisa = log(saliva_elisa_value + saliva_ELISA_log_shift)) 
    

  aedes_survey_cleaned_v1_v5 <- aedes_survey_cleaned[!duplicated(aedes_survey_cleaned$study_id), ] %>% 
      mutate(visit = "Visit 5") %>% 
      mutate(visit_date = as.Date("2020-07-01")) %>% 
      mutate(visit_date_abr = NA) %>% 
      mutate(wet_season = "yes") %>% 
      mutate(visit_year = 2) %>% 
      select(-c(saliva_elisa_value, log_saliva_elisa)) %>% 
      full_join(aedes_visit5) %>% 
      select(colnames(aedes_survey_cleaned)) %>% 
      bind_rows(aedes_survey_cleaned) %>% 
      arrange(study_id, visit_date)
  
  
  aedes_coord_og <- read_csv(here("data", "PAGODAS_Coordinates.csv"), show_col_types = FALSE)
  
  aedes_coord_cleaned <- aedes_coord_og %>%
    clean_names()
  
  aedes_full <- full_join(aedes_survey_cleaned_v1_v5, aedes_coord_cleaned) %>% 
    filter(sched_visit == "yes") %>% 
    mutate(visit = case_when(
      visit == "VISIT 1 DENGUE INDEX" ~ "visit1",
      visit == "VISIT 2  DENGUE INDEX" ~ "visit2",
      visit == "VISIT 3 DENGUE INDEX" ~ "visit3",
      visit == "VISIT 4 INDEX" ~ "visit4",
      visit == "Visit 5" ~ "visit5",
      TRUE ~ "NA"
    ))

  aedes_survey_with_river <- read_csv(here("data", "DistPHHtoRiver.csv"), show_col_types = FALSE) %>% 
    select(study_id = Study.ID, distance_to_river = distance) %>%
    mutate(distance_to_river_scaled = (distance_to_river - mean(distance_to_river)) / sd(distance_to_river)) %>% 
    mutate(close_to_river = factor(
      ifelse(distance_to_river <= params$near_river_cut_off, "yes", "no"), 
      levels = c("no", "yes")
    )) %>% 
    right_join(aedes_full)
  
  
  aedes_red <- aedes_survey_with_river %>% 
    filter(!is.na(saliva_elisa_value)) %>% 
    filter(!is.na(visit_date)) %>% 
    filter(school_attended_all != "NA") %>% 
    mutate(num_domestic_water_containers_in_home = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = num_domestic_water_containers_in_home
    )) %>% 
    mutate(num_toilets_in_home = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = num_toilets_in_home
    )) %>% 
    mutate(how_often_use_bed_net = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(how_often_use_bed_net)
    )) %>% 
    mutate(insecticide_spray = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(insecticide_spray)
    )) %>%
    mutate(larvicide_applied_to_water = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(larvicide_applied_to_water)
    )) %>%
    mutate(how_often_mosquito_coils_burned = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(how_often_mosquito_coils_burned)
    ))

  
  time_varying <- read_xlsx(here("data", "AllVisitDataWithScheDengueRiskFactors.xlsx")) %>% 
    select(
      study_id = "Study ID", 
      visit = "Event Name",
      num_domestic_water_containers_in_home = "1. How many domestic water containers are in the subject's home?",
      num_toilets_in_home = "2. How many toilets are in the subject's home?",
      how_often_use_bed_net = "3. How often does the subject use a bed net?",
      insecticide_spray = "4. Is the subject's home sprayed with insecticide?",
      larvicide_applied_to_water = "5. Is larvicide applied to water containers at the subject's home?",
      how_often_mosquito_coils_burned = "6. How often are mosquito coils burned in the subject's house?",
    ) %>% 
    mutate(visit = gsub(" ", "", str_to_lower(visit), fixed = TRUE)) %>%
    filter(visit != "visit6") %>% 
    filter(!(study_id == "100-0468" & visit == "visit4")) %>% # Missing data
    mutate(num_domestic_water_containers_in_home = as.numeric(num_domestic_water_containers_in_home)) %>% 
    mutate(num_toilets_in_home = as.numeric(num_toilets_in_home)) %>% 
    mutate(how_often_use_bed_net = as.character(factor(
      how_often_use_bed_net,
      levels = c(
        "Never", 
        "Rarely", 
        "Regularly/ Most of the time", 
        "All the time"
      ),
      labels = c(
        "Never", 
        "Rarely", 
        "Most of the time", 
        "All of the time"
      )
    ))) %>% 
    mutate(how_often_mosquito_coils_burned = as.character(factor(
      how_often_mosquito_coils_burned,
      levels = c(
        "Never", 
        "Rarely (about 1x/month)", 
        "Sometimes (about 1x/week)",
        "Often (about 3x/week)",
        "Daily"
      ),
      labels = c(
        "Never", 
        "~ 1x/month", 
        "~ 1x/week",
        "~ 3x/week",
        "Daily"
      )
    )))
  
  time_varying_vars <- c("num_domestic_water_containers_in_home", "num_toilets_in_home", "how_often_use_bed_net", "insecticide_spray", "larvicide_applied_to_water", "how_often_mosquito_coils_burned")
  
  
  aedes_red <- aedes_red %>% 
    filter(visit != "visit1") %>% 
    select(-time_varying_vars) %>% 
    left_join(time_varying) %>% 
    select(colnames(aedes_red)) %>% 
    bind_rows(aedes_red %>% filter(visit == "visit1")) %>% 
    mutate(visit = factor(visit)) %>% 
    mutate(visit5 = factor(ifelse(visit != "visit5", "no", "yes"))) %>% 
    mutate(wet_season = factor(wet_season, levels = c("no", "yes"))) %>% 
    filter(!is.na(num_domestic_water_containers_in_home)) %>% 
    mutate(how_often_use_bed_net = factor(
      how_often_use_bed_net,
      levels = c(
        "Never", 
        "Rarely", 
        "Most of the time", 
        "All of the time"
      )
    )) %>% 
    mutate(insecticide_spray = factor(insecticide_spray)) %>% 
    mutate(larvicide_applied_to_water = factor(larvicide_applied_to_water)) %>% 
    mutate(how_often_mosquito_coils_burned = factor(
      how_often_mosquito_coils_burned,
      levels = c(
        "Never", 
        "~ 1x/month", 
        "~ 1x/week",
        "~ 3x/week",
        "Daily"
      )
    ))
  
  
  aedes_red <- read_csv(here("data", "PAGODAS_Landtype.csv")) %>% 
    select(-c(X, Y, lon, lat, elevation)) %>% 
    clean_names() %>% 
    mutate(modal_land_type = factor(
      str_to_lower(modal_land_type), 
      levels = c("urban", "rice paddy", "cropland")
    )) %>% 
    right_join(aedes_red, by = "study_id")
  
  
  #### Incorporate satellite data
  max_date_diff <- 60
  date_lag <- params$modis_lag
  
  
  sat_data500 <- process_modis_data(
    df_og = read_csv(here("data", "MODIS_500m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 7
  ) %>% 
    arrange(Study.ID, var_type, date)
  
  
  sat_df <- sat_data500
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    df_id <- sat_df %>% 
      filter(Study.ID == as.character(df_og[i, "study_id"]))
    
    for(j in 1:num_vars) {
      df_id_var <- df_id %>% 
        filter(var_type == var_types[j])
      
      if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
        date_diff <- (df_og$visit_date[i] - days(date_lag)) - df_id_var$date
        curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
        
        if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
          print(paste0(
            "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
            var_types[j], " value available within ", max_date_diff, 
            " days [max_date_diff] of ", date_lag, " days [date_lag] prior to visit date!"
          ))
        } else {
          df_new[i, var_types[j]] <- curr$sat_var_value
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI500_home = EVI, NVI500_home = NVI, NFI500_home = NFI)
  
  
  #### Incorporate satellite data 
  sat_data250 <- process_modis_data(
    df_og = read_csv(here("data", "MODIS_250m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 7
  )
  
  
  sat_df <- sat_data250
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    df_id <- sat_df %>% 
      filter(Study.ID == as.character(df_og[i, "study_id"]))
    
    for(j in 1:num_vars) {
      df_id_var <- df_id %>% 
        filter(var_type == var_types[j])
      
      if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
        date_diff <- (df_og$visit_date[i] - days(date_lag)) - df_id_var$date
        curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
        
        if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
          print(paste0(
            "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
            var_types[j], " value available within ", max_date_diff, 
            " days [max_date_diff] of ", date_lag, " days [date_lag] prior to visit date!"
          ))
        } else {
          df_new[i, var_types[j]] <- curr$sat_var_value
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI250_home = EVI, NVI250_home = NVI, NFI250_home = NFI)
  
  
    #### Incorporate satellite data 16 days
  sat_data250 <- process_modis_data(
    df_og = read_csv(here("data", "MODIS_250m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 7
  )
  
  
  sat_df <- sat_data250
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    df_id <- sat_df %>% 
      filter(Study.ID == as.character(df_og[i, "study_id"]))
    
    for(j in 1:num_vars) {
      df_id_var <- df_id %>% 
        filter(var_type == var_types[j])
      
      if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
        date_diff <- (df_og$visit_date[i] - days(16)) - df_id_var$date
        curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
        
        if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
          print(paste0(
            "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
            var_types[j], " value available within ", max_date_diff, 
            " days [max_date_diff] of ", 16, " days [16] prior to visit date!"
          ))
        } else {
          df_new[i, var_types[j]] <- curr$sat_var_value
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI250_home16 = EVI, NVI250_home16 = NVI, NFI250_home16 = NFI)
  
  
      #### Incorporate satellite data 48 days
  sat_data250 <- process_modis_data(
    df_og = read_csv(here("data", "MODIS_250m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 7
  )
  
  
  sat_df <- sat_data250
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    df_id <- sat_df %>% 
      filter(Study.ID == as.character(df_og[i, "study_id"]))
    
    for(j in 1:num_vars) {
      df_id_var <- df_id %>% 
        filter(var_type == var_types[j])
      
      if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
        date_diff <- (df_og$visit_date[i] - days(48)) - df_id_var$date
        curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
        
        if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
          print(paste0(
            "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
            var_types[j], " value available within ", max_date_diff, 
            " days [max_date_diff] of ", 48, " days [48] prior to visit date!"
          ))
        } else {
          df_new[i, var_types[j]] <- curr$sat_var_value
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI250_home48 = EVI, NVI250_home48 = NVI, NFI250_home48 = NFI)
  
  
  #### Incorporate school satellite data 
  sat_data250 <- process_modis_data(
    df_og = read_csv(here("data", "SchoolsMODIS_250m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 6
  ) %>% 
    mutate(names = ifelse(
      names == "Kindergarten<U+200B> Salon", 
      yes = "Kindergarten​ Salon", 
      no = names
    ))
  
  
  sat_df <- sat_data250
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    if(df_og[i, "school_attended_all"] != "Subject Not In School") {
      df_id <- sat_df %>% 
        filter(names == as.character(df_og[i, "school_attended_all"]))
      
      for(j in 1:num_vars) {
        df_id_var <- df_id %>% 
          filter(var_type == var_types[j])
        
        if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
          date_diff <- (df_og$visit_date[i] - days(date_lag)) - df_id_var$date
          curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
          
          if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
            print(paste0(
              "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
              var_types[j], " value available within ", max_date_diff, 
              " days [max_date_diff] of ", date_lag, " days [date_lag] prior to visit date!"
            ))
          } else {
            df_new[i, var_types[j]] <- curr$sat_var_value
          }
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI250_sch = EVI, NVI250_sch = NVI, NFI250_sch = NFI) %>% 
    mutate(EVI250_sch = ifelse(is.na(EVI250_sch), yes = 0, no = EVI250_sch)) %>% 
    mutate(NVI250_sch = ifelse(is.na(NVI250_sch), yes = 0, no = NVI250_sch)) %>% 
    mutate(NFI250_sch = ifelse(is.na(NFI250_sch), yes = 0, no = NFI250_sch))                 
  
  aedes_red <- aedes_red[!is.na(aedes_red$NVI250_home), ]
  
  
   #### Incorporate school satellite data 16
  sat_data250 <- process_modis_data(
    df_og = read_csv(here("data", "SchoolsMODIS_250m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 6
  ) %>% 
    mutate(names = ifelse(
      names == "Kindergarten<U+200B> Salon", 
      yes = "Kindergarten​ Salon", 
      no = names
    ))
  
  
  sat_df <- sat_data250
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    if(df_og[i, "school_attended_all"] != "Subject Not In School") {
      df_id <- sat_df %>% 
        filter(names == as.character(df_og[i, "school_attended_all"]))
      
      for(j in 1:num_vars) {
        df_id_var <- df_id %>% 
          filter(var_type == var_types[j])
        
        if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
          date_diff <- (df_og$visit_date[i] - days(16)) - df_id_var$date
          curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
          
          if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
            print(paste0(
              "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
              var_types[j], " value available within ", max_date_diff, 
              " days [max_date_diff] of ", 16, " days [16] prior to visit date!"
            ))
          } else {
            df_new[i, var_types[j]] <- curr$sat_var_value
          }
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI250_sch16 = EVI, NVI250_sch16 = NVI, NFI250_sch16 = NFI) %>% 
    mutate(EVI250_sch16 = ifelse(is.na(EVI250_sch16), yes = 0, no = EVI250_sch16)) %>% 
    mutate(NVI250_sch16 = ifelse(is.na(NVI250_sch16), yes = 0, no = NVI250_sch16)) %>% 
    mutate(NFI250_sch16 = ifelse(is.na(NFI250_sch16), yes = 0, no = NFI250_sch16))                 
  
  
  aedes_red <- aedes_red %>% 
    mutate(lat_s = (lat - mean(lat)) / sd(lat)) %>% 
    mutate(lon_s = (lon - mean(lon)) / sd(lon)) %>% 
    mutate(time = as.numeric(case_when(
      visit == "visit1" ~ 1,
      visit == "visit2" ~ 2,
      visit == "visit3" ~ 3,
      visit == "visit4" ~ 4,
      visit == "visit5" ~ 5
    ))) %>% 
    mutate(visit_year_cat = factor(as.character(visit_year), levels = c("0", "1", "2")))
  
  
  saveRDS(aedes_red, file = here("data", "processed_aedes_data.rds"))
  
}
  

aedes_red_ind <- aedes_red %>%
  filter(visit == "visit1") %>% 
  mutate(visit = droplevels(visit))
```


## Individual visit surfaces  
```{r prep_and_fit_visit_surf_model_func}
prep_and_fit_visit_surf_model <- function(data = aedes_red, visit_name, mesh_to_grid_dims){
  grid_dims_prod <- mesh_to_grid_dims[1] * mesh_to_grid_dims[2]
  
  
  ## extract relevant data (not sure if sorting is necessary)
  coords_st <- data %>% 
    arrange(study_id) %>% 
    filter(visit == visit_name) %>% 
    select(
      lon = x, lat = y, 
      log_saliva_elisa,
    )
    
  ## specify df of covariate values including intercept
  covar_df <- data.frame(
    Intercept = rep(1, nrow(coords_st)),
    select(coords_st, -c(lon, lat, log_saliva_elisa))
  )
      
  ## extract coordinates as matrix, ignoring repeats
  coords <- select(coords_st, lon, lat) %>% 
    distinct() %>% 
    as.matrix()
    
  ## create mesh, good documentation available to understand all options
  mesh <- inla.mesh.2d(
    loc = coords,
    max.edge = c(300, 600)
  )
    
    
  ## specify spde
  spde <- inla.spde2.matern(mesh)
    
  # Need to specify index with spde and group (if there are replicates)
  s.index <- inla.spde.make.index(
    "spatial.field", 
    n.spde = spde$n.spde,
    n.group = 1
  )
    
  ## A specifies something about edge length based on the mesh
  A <- inla.spde.make.A(
    mesh = mesh, 
    loc = as.matrix(select(coords_st, lon, lat))
  )
    
  ## Prep data for inla call, "A" needs to have a 1 for each list element in effects, aside from index. 
  data_stack <- inla.stack(
    data = list(y = coords_st$log_saliva_elisa),
    A = list(A, 1),
    effects = list(s.index, list(covar_df = covar_df)),
    tag = "est"
  )
    
    
  ## specify model formula, 'f()' incorporates spatial effect and replicate 
  formula <- y ~ 0 + Intercept +
    f(
      spatial.field, 
      model = spde
    )
      
    
  ## fixed effect priors
  coeff_priors <- list(
    mean.intercept = 0,
    prec.intercept = 1/(2.5^2),
    mean = list(default = 0),
    prec = list(default = 1/(2.5^2))
  )
    
    
  ## This is with a grid
  proj_grid <- inla.mesh.projector(
    mesh, 
    # xlim = range(mesh$loc[, 1]), 
    # ylim = range(mesh$loc[, 2]),
    dims = mesh_to_grid_dims
  )
    
  pred_stack <- inla.stack(
    data = list(y = NA),
    A = list(proj_grid$proj$A, 1),
    effects = list(
      s.index, 
      Intercept = rep(1, grid_dims_prod)
    ),
    tag = "pred"
  )
    
    
  full_stack <- inla.stack(data_stack, pred_stack)
    
    
  ## Fit model
  visit_fit <- inla(
    formula, 
    data = inla.stack.data(full_stack),
    control.predictor = list(A = inla.stack.A(full_stack), compute = TRUE),
    control.fixed = coeff_priors,
    control.results = list(
      return.marginals.random = FALSE,
      return.marginals.predictor = TRUE
    )
  )
    
    
  ## Extract indices of observations predictions were made for
  pred_index <- inla.stack.index(full_stack, "pred")$data
    
    
  ## Extract prediction means, sd, and 0.025 and 0.975 quantiles
  visit_preds <- visit_fit$summary.fitted.values[pred_index, c(1:3, 5)]
  
  
  preds_df <- bind_rows(
    data.frame(proj_grid$lattice$loc, "pred" = visit_preds$`0.025quant`) %>% 
      select(lon = X1, lat = X2, pred) %>% 
      mutate(type = rep("ci_lb0.025", grid_dims_prod)),
    data.frame(proj_grid$lattice$loc, "pred" = visit_preds$`0.975quant`) %>% 
        select(lon = X1, lat = X2, pred) %>% 
        mutate(type = rep("ci_ub0.975", grid_dims_prod)),
    data.frame(proj_grid$lattice$loc, "pred" = visit_preds$mean) %>% 
      select(lon = X1, lat = X2, pred) %>% 
      mutate(type = rep("mean", grid_dims_prod))
  ) %>% 
    mutate(type = factor(type, levels = c("ci_lb0.025", "mean", "ci_ub0.975")))
  
  
  list("visit_fit" = visit_fit, "preds_df" = preds_df)
}
```


```{r ind-visit-surf-fit}
if(params$refit_vistit_fit) {
  
  v1_fit <- prep_and_fit_visit_surf_model(
    visit_name = "visit1", 
    mesh_to_grid_dims = c(101, 101)
  )
  
   v2_fit <- prep_and_fit_visit_surf_model(
    visit_name = "visit2",
    mesh_to_grid_dims = c(101, 101)
  )
  
   v3_fit <- prep_and_fit_visit_surf_model(
    visit_name = "visit3",
    mesh_to_grid_dims = c(101, 101)
  )
   
  v4_fit <- prep_and_fit_visit_surf_model(
    visit_name = "visit4",
    mesh_to_grid_dims = c(101, 101)
  )
  
  v5_fit <- prep_and_fit_visit_surf_model(
    visit_name = "visit5",
    mesh_to_grid_dims = c(101, 101)
  )
  
  ind_visit_surf_df_og <- rbind(
  cbind(v1_fit$preds_df, "visit" = rep("Visit 1", nrow(v1_fit$preds_df))), 
  cbind(v2_fit$preds_df, "visit" = rep("Visit 2", nrow(v2_fit$preds_df))), 
  cbind(v3_fit$preds_df, "visit" = rep("Visit 3", nrow(v3_fit$preds_df))), 
  cbind(v4_fit$preds_df, "visit" = rep("Visit 4", nrow(v4_fit$preds_df))), 
  cbind(v5_fit$preds_df, "visit" = rep("Visit 5", nrow(v5_fit$preds_df)))
) %>% 
  mutate(type = factor(
    case_when(
      type == "ci_lb0.025" ~ "CI 95% LB", 
      type == "mean" ~ "Mean",
      type == "ci_ub0.975" ~ "CI 95% UB"
    ),
    levels = c("CI 95% LB", "Mean", "CI 95% UB")
  )) %>% 
  mutate(Prediction = pred) %>% 
  mutate(x_m = lon) %>%
  mutate(y_m = lat) %>% 
  select(-c("pred", "lon", "lat"))
  
  
  ## Get UTMs from coordinates
  utm_ex <- SpatialPoints(
    as.matrix(select(ind_visit_surf_df_og, x_m, y_m)),
    proj4string = CRS("+proj=utm +zone=48")
  )
  
  lat_lon <- coordinates(spTransform(utm_ex, CRS("+proj=longlat")))
  
  ind_visit_surf_df <- data.frame(
    ind_visit_surf_df_og,
    lon = lat_lon[, "x_m"],
    lat = lat_lon[, "y_m"]
  )
  
  
  saveRDS(ind_visit_surf_df, here("output", "ind_visit_surf_df.rds"))
  
} else {
  
  ind_visit_surf_df <- readRDS(here("output", "ind_visit_surf_df.rds"))
  
}

fit_y <- lm(y_m ~ lat, data = ind_visit_surf_df)

y_coef <- as.vector(fit_y$coefficients)

lat_labels <- c(11.45, 11.46, 11.47)

lat_breaks <- c(
  y_coef[1] + y_coef[2] * lat_labels[1], 
  y_coef[1] + y_coef[2] * lat_labels[2], 
  y_coef[1] + y_coef[2] * lat_labels[3]
)

fit_x <- lm(x_m ~ lon, data = ind_visit_surf_df)

x_coef <- as.vector(fit_x$coefficients)

lon_labels <- c(104.51, 104.53, 104.55)

lon_breaks <- c(
  x_coef[1] + x_coef[2] * lon_labels[1], 
  x_coef[1] + x_coef[2] * lon_labels[2], 
  x_coef[1] + x_coef[2] * lon_labels[3]
)
```


```{r google-map, eval = FALSE}
sat_map <- get_googlemap(center = c(lon = 104.53, lat = 11.46), maptype = "terrain")
```


```{r plot_visit_predictions-without-cis}
pdf(here("output", "visit-prediction-surfaces-wo-ci.pdf"), width = 10)

ind_visit_surf_df %>% 
  filter(type == "Mean") %>% 
  filter(visit != "Visit 5") %>% 
  filter(x_m >= x_coef[1] + x_coef[2] * 104.50 & x_m <= x_coef[1] + x_coef[2] * 104.56) %>% 
  filter(y_m >= y_coef[1] + y_coef[2] * 11.44 & y_m <= y_coef[1] + y_coef[2] * 11.48) %>% 
ggplot() +
  geom_raster(mapping = aes(x = x_m, y = y_m, fill = Prediction)) +
  facet_grid(~ visit) +
  coord_equal() +
  scale_fill_viridis() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme_bw() +
  theme(
    strip.background = element_rect(fill = NA),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "white"),
    panel.background = element_rect(fill = NA),
    panel.ontop = TRUE,
    panel.border = element_blank(),
    legend.position = "bottom"
  ) +
  scale_y_continuous(breaks = lat_breaks, labels = lat_labels) +
  scale_x_continuous(breaks = lon_breaks, labels = lon_labels)

dev.off()
```


```{r plot_visit_predictions-with-cis}
pdf(here("output", "visit-prediction-surfaces-w-ci.pdf"), width = 10)

ind_visit_surf_df %>% 
  filter(visit != "Visit 5") %>% 
  filter(x_m >= x_coef[1] + x_coef[2] * 104.50 & x_m <= x_coef[1] + x_coef[2] * 104.56) %>% 
  filter(y_m >= y_coef[1] + y_coef[2] * 11.44 & y_m <= y_coef[1] + y_coef[2] * 11.48) %>% 
ggplot() +
  geom_raster(mapping = aes(x = x_m, y = y_m, fill = Prediction)) +
  facet_grid(type ~ visit) +
  coord_equal() +
  scale_fill_viridis() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme_bw() +
  theme(
    strip.background = element_rect(fill = NA),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "white"),
    panel.background = element_rect(fill = NA),
    panel.ontop = TRUE,
    panel.border = element_blank(),
    legend.position = "bottom"
  ) +
  scale_y_continuous(breaks = lat_breaks, labels = lat_labels) +
  scale_x_continuous(breaks = lon_breaks, labels = lon_labels)

dev.off()
```


```{r display-visit-prediction-surfaces-wo-v5-plot, eval = TRUE, fig.align='center', out.width='100%', fig.cap='Prediction surfaces of mean Aedes mosquito exposure by visit, without visit 5.'}
knitr::include_graphics(here("output", "visit-prediction-surfaces-wo-v5.pdf"))
```



\newpage 

## Main model
Full model equation:

\begin{equation*}
  \begin{split}
    \log(\text{Saliva antibody response})_{ij} &= \beta_0 + \boldsymbol{\beta} *(\\
    &\text{Gender}_i + \text{Age}_i  + \text{Distance to river}_i + \text{Land type}_i\\
    &+\text{Toilets}_i + \text{Water containers}_i + \text{Insecticide}_i + \text{Larval containers}_i\\
    &+ \text{NFI}_{ij} + \text{Wet season}_{ij})
  \end{split}
\end{equation*}

`Gender` Indicator for gender (female and male only)  
`Age` Baseline age centered at 7 years old  
`Modal land type` This is the modal land type across *?* pixels around house; has 3 levels: "urban", "rice paddy", "cropland".  
`Distance to river` Distance in meters from house to nearest part of the stream; centered and scaled  
`Insecticide use` Indicator for use of insecticide spray  
`Larvicide use` Indicator for use of larvicide spray applied to water  
`Number of toilets` Number of toilets in house  
`Number of water containers` Number of domestic water containers in house  
`Wet season` Indicator for visit date being in wet season  
`NFI (flooding index)` Mean flooding index for a 250 meter buffer around house 32 days prior to visit date


```{r main-model-prep-wov5}
## extract relevant data (not sure if sorting is necessary)
coords_st <- aedes_red %>% 
  filter(visit != "visit5") %>% 
  arrange(study_id, time) %>% 
  select(
    time, 
    lon = x, lat = y, 
    log_saliva_elisa,
    gender,
    age_cented7, distance_to_river_scaled,
    modal_land_type,
    num_toilets_in_home, num_domestic_water_containers_in_home,
    insecticide_spray, larvicide_applied_to_water,
    NFI250_home,
    wet_season
  )

## specify df of covariate values including intercept
covar_df <- data.frame(
  # Intercept = rep(1, nrow(coords_st)),
  select(coords_st, -c(time, lon, lat, log_saliva_elisa))
)
  
## extract coordinates as matrix, ignoring repeats
coords <- select(coords_st, lon, lat) %>% 
  distinct() %>% 
  as.matrix()

## create mesh, good documentation available to understand all options
mesh <- inla.mesh.2d(
  loc = coords,
  max.edge = c(300, 600)
)

# specify spde
spde <- inla.spde2.matern(mesh)

# Need to specify index with spde and group (if there are replicates)
s.index <- inla.spde.make.index(
  "spatial.field", 
  n.spde = spde$n.spde,
  n.group = 4
)

## A specifies something about edge length based on the mesh
A <- inla.spde.make.A(
  mesh = mesh, 
  loc = as.matrix(select(coords_st, lon, lat)), 
  group = coords_st$time
)

## Prep data for inla call, "A" needs to have a 1 for each list element in effects, aside from index
stack <- inla.stack(
  data = list(y = coords_st$log_saliva_elisa),
  A = list(A, 1),
  effects = list(
    s.index,
    list(covar_df = covar_df)
  ),
  tag = "est"
)

## specify model formula, 'f()' incorporates spatial effect and replicate 
formula <- y ~ #0 + Intercept
  gender + 
  age_cented7  + distance_to_river_scaled +
  modal_land_type +
  num_toilets_in_home + num_domestic_water_containers_in_home +
  insecticide_spray + larvicide_applied_to_water  +
  NFI250_home  +
  wet_season +
  f(
    spatial.field, 
    model = spde, 
    group = spatial.field.group, 
    control.group = list(model = "iid")
  )
  

## fixed effect priors
coeff_priors <- list(
    mean.intercept = 0,
    prec.intercept = 1/(2.5^2),
    mean = list(default = 0),
    prec = list(default = 1/(2.5^2))
)
```


```{r main-model-wov5, eval = TRUE}
if(params$refit_fit) {
  main_fit_wov5 <- inla(
    formula, 
    data = inla.stack.data(stack),
    control.predictor = list(
      A = inla.stack.A(stack),
      compute = TRUE
    ),
    control.fixed = coeff_priors
  )
  
  # Warning in inla(formula, data = inla.stack.data(stack), control.predictor = list(A = inla.stack.A(stack)),  :
  # The A-matrix in the predictor (see ?control.predictor) is specified
  # but an intercept is in the formula. This will likely result
  # in the intercept being applied multiple times in the model, and is likely
  # not what you want. See ?inla.stack for more information.
  # You can remove the intercept adding ``-1'' to the formula.
  
  
  ## Check that pred_rownames and pred_name_vec line up
pred_rownames_ordered <- c(
  "(Intercept)",
  "genderMale",
  "age_cented7",
  "insecticide_sprayYes",
  "larvicide_applied_to_waterYes",
  "num_toilets_in_home",
  "num_domestic_water_containers_in_home",
  "modal_land_typerice paddy",
  "modal_land_typecropland",
  "distance_to_river_scaled",
  "wet_seasonyes",
  "NFI250_home"
)

pred_names_vec = c(
  "(Intercept)",
  "Male", 
  "Age (centered at 7)", 
  "Insecticide used",
  "Larvicide used",
  "Number of toilets in home",
  "Number of water containers in home",
  "Rice paddy",
  "Cropland",
  "Distance to river (std. dev.)", 
  "Wet season",
  "Normalized flooding index"
)


  main_fit_df <- main_fit_wov5$summary.fixed %>% 
    mutate(unordered_names = rownames(main_fit_wov5$summary.fixed)) %>% 
    mutate(pred_names = factor(
      unordered_names,
      levels = pred_rownames_ordered,
      labels = pred_names_vec
    )) %>% 
    arrange(pred_names) %>% 
    select(quant025 = "0.025quant", mean = "mean", quant975 = "0.975quant", pred_names)

  write.csv(main_fit_df, here("output", "main_fit_df.csv"))
} else {
  main_fit_df <- read.csv(here("output", "main_fit_df.csv"))
  rownames(main_fit_df) <- main_fit_df$X
  main_fit_df <- main_fit_df[, -1]
}
```


```{r main-model-table-data-prep, eval = TRUE}
total_n <- nrow(aedes_red_ind)

aedes_red_wo5 <- filter(aedes_red, visit != "visit5") %>% mutate(visit = droplevels(visit))
visit_n_df <- group_by(aedes_red_wo5, visit) %>% summarize(group_n = n())


## Visit 1 summary statistics
visit1_summary <- bind_rows(
  ## Gender
  aedes_red_ind %>% group_by(gender) %>% summarize(count_n = n()) %>% 
    mutate(variable1 = "Gender") %>% mutate(variable2 = gender) %>% 
    mutate(visit1 = paste0(
      count_n, " (", round(100 * count_n / total_n, 2), "%)")
    ) %>% 
    select(variable1, variable2, visit1) %>% 
    mutate(pred_names = c("Female", "Male")),
  ## Age
  data.frame(
    variable1 = " ", 
    variable2 = "Age",
    visit1 = paste0(
      round(mean(aedes_red_ind$age), 2), " (", round(sd(aedes_red_ind$age), 2), ")"
    )
  ) %>% 
    mutate(pred_names = "Age (centered at 7)"),
  ## Land type
  aedes_red_ind %>% group_by(modal_land_type) %>% summarize(count_n = n()) %>% 
    mutate(variable1 = "Land type") %>% mutate(variable2 = modal_land_type) %>% 
    mutate(visit1 = paste0(
      count_n, " (", round(100 * count_n / total_n, 2), "%)"
    )) %>% 
    select(variable1, variable2, visit1) %>% 
    mutate(pred_names = c("Urban", "Rice paddy", "Cropland")),
  ## Distance to river
  data.frame(
    variable1 = " ", 
    variable2 = "Distance to river (std.)",
    visit1 = paste0(
      round(mean(aedes_red_ind$distance_to_river_scaled), 2), " (", round(sd(aedes_red_ind$distance_to_river_scaled), 2), ")"
    )
  ) %>% 
    mutate(pred_names = "Distance to river (std. dev.)")
) %>% 
  mutate(variable2 = str_to_sentence(variable2)) %>% 
  mutate(visit2 = "") %>% mutate(visit3 = "") %>% mutate(visit4 = "")


all_visits_summary <- bind_rows(
  ## Insecticide spray
  aedes_red_wo5 %>% 
    group_by(visit, insecticide_spray) %>% summarize(count_n = n()) %>% 
    left_join(visit_n_df) %>% 
    mutate(col_summary = paste0(
      count_n, " (", round(100 * count_n / group_n, 2), "%)"
    )) %>%
    mutate(variable1 = "Insecticide") %>% mutate(variable2 = insecticide_spray) %>% 
    select(variable1, variable2, visit, col_summary) %>% 
    pivot_wider(names_from = visit, values_from = col_summary, values_fill = "") %>% 
    mutate(pred_names = c("Insecticide not used", "Insecticide used")),
  ## Larvicide spray
   aedes_red_wo5 %>% 
    group_by(visit, larvicide_applied_to_water) %>% summarize(count_n = n()) %>% 
    left_join(visit_n_df) %>% 
    mutate(col_summary = paste0(
      count_n, " (", round(100 * count_n / group_n, 2), "%)"
    )) %>%
    mutate(variable1 = "Larvicide") %>% mutate(variable2 = larvicide_applied_to_water) %>% 
    select(variable1, variable2, visit, col_summary) %>% 
    pivot_wider(names_from = visit, values_from = col_summary, values_fill = "") %>% 
    mutate(pred_names = c("Larvicide not used", "Larvicide used")),
  ## Toilets
  aedes_red_wo5 %>% 
    group_by(visit) %>% 
    summarize(mean = mean(num_toilets_in_home), sd = sd(num_toilets_in_home)) %>% 
    mutate(col_summary = paste0(round(mean, 2), " (", round(sd, 2), ")")) %>% 
    mutate(variable1 = "") %>% mutate(variable2 = "Toilets") %>% 
    select(variable1, variable2, visit, col_summary) %>% 
    pivot_wider(names_from = visit, values_from = col_summary, values_fill = "") %>% 
    mutate(pred_names = "Number of toilets in home"),
  ## Water containers
  aedes_red_wo5 %>% 
    group_by(visit) %>% 
    summarize(mean = mean(num_domestic_water_containers_in_home), sd = sd(num_domestic_water_containers_in_home)) %>% 
    mutate(col_summary = paste0(round(mean, 2), " (", round(sd, 2), ")")) %>% 
    mutate(variable1 = "") %>% mutate(variable2 = "Water containers") %>% 
    select(variable1, variable2, visit, col_summary) %>% 
    pivot_wider(names_from = visit, values_from = col_summary, values_fill = "") %>% 
    mutate(pred_names = "Number of water containers in home"),
  ## Wet season
  bind_rows(data.frame(
    variable1 = rep("Wet season", 2),
    variable2 = c("No", "Yes"),
    visit1 = c("0", paste0(visit_n_df$group_n[1])),
    visit2 = c(paste0(visit_n_df$group_n[2]), "0"),
    visit3 = c("0", paste0(visit_n_df$group_n[3])),
    visit4 = c(paste0(visit_n_df$group_n[4]), "0")
  )) %>% 
    mutate(pred_names = c("Wet season no", "Wet season")),
  ## NFI
  aedes_red_wo5 %>% 
    group_by(visit) %>% 
    summarize(mean = mean(NFI250_home), sd = sd(NFI250_home)) %>% 
    mutate(col_summary = paste0(round(mean, 2), " (", round(sd, 2), ")")) %>% 
    mutate(variable1 = "") %>% mutate(variable2 = "Flooding index (NFI)") %>% 
    select(variable1, variable2, visit, col_summary) %>% 
    pivot_wider(names_from = visit, values_from = col_summary, values_fill = "") %>% 
    mutate(pred_names = "Normalized flooding index")
)
  


main_est <- main_fit_df %>% 
  filter(pred_names != "(Intercept)") %>% 
  mutate(Estimate = paste0(
    round(mean, 3), " (", round(quant025, 3 ), ", ", round(quant975, 3), ")"
  )) %>% 
  select(Estimate, pred_names)

main_results_table <- bind_rows(visit1_summary, all_visits_summary) %>% 
  full_join(main_est, by = "pred_names") %>% 
  mutate(Estimate = ifelse(is.na(Estimate), "Reference", Estimate)) %>% 
  select(-pred_names) 

write.csv(main_results_table, here("output", "main-model-results-table.csv"))
```


```{r main-model-results-table, eval = TRUE}
main_results_table %>% 
  select(-c("variable1")) %>% 
kbl(
  #booktabs = TRUE, 
  col.names = c(" ", "Visit 1", "Visit 2", "Visit 3", "Visit 4", "Mean Estimate (95% BCI)")
) %>% 
  kable_styling() %>% 
  pack_rows(
    index = c(
      "Gender" = 2,
      " " = 1,
      "Land type" = 3,
      " " = 1,
      "Insecticide" = 2,
      "Larvicide" = 2,
      " " = 2,
      "Wet season" = 2,
      " " = 1
    ), 
    bold = FALSE
  )
```


\newpage
```{r main-model-forest-plot-wov5}
pdf(here("output", "main-model-forest-plot-wo-v5.pdf"))

main_fit_plot_df <- main_fit_df %>% 
  filter(pred_names != "(Intercept)") %>% 
  add_row(pred_names = "Sex [ref: Female]", .before = 1) %>% 
  add_row(pred_names = "Modal land type [ref: Urban]", .before = 4) %>% 
  mutate(pred_names = factor(pred_names, levels = pred_names))

main_fit_plot_df %>% 
  ggplot(aes(x = mean, y = pred_names)) +
    geom_point() +
    geom_linerange(aes(xmin = quant025, xmax = quant975)) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    theme_bw(base_size = 12, base_family = 'Times New Roman') +
    theme(
      panel.border = element_blank(),
      axis.text.y = element_text(hjust = 0, color = "black"),
      axis.ticks.y = element_blank(),
      axis.text.x=element_text(color = "black"),
      panel.grid.major = element_line(colour = "gray90")
    ) +
    xlab("") +
    ylab("") +
  scale_y_discrete(limits = rev)

dev.off()
```

```{r load-main-model-forest-plot-wov5, eval = TRUE, fig.cap="Full model results, estimated mean and BCI"}
include_graphics(here("output", "main-model-forest-plot-wo-v5.pdf"))
```
