---
title: "Aedes serology investigation"
geometry: margin=0.5cm
output: pdf_document
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
params:
  rerun_data: FALSE
  near_river_cut_off: 300
  modis_lag: 30
  rerun_fit1_bayes: FALSE
  rerun_fit2_bayes: FALSE
  rerun_fit3_bayes: FALSE
  rerun_fit4_bayes: FALSE
  rerun_fit1_freq: FALSE
  rerun_fit2_freq: FALSE
  rerun_fit3_freq: FALSE
  rerun_fit4_freq: FALSE
  rerun_fit5_bayes: FALSE
  rerun_fit6_bayes: FALSE
  rerun_fit7_bayes: FALSE
  rerun_fit_young: FALSE
  rerun_fit_school: FALSE
  fit_main: FALSE
  rerun_fit_v1_surf: FALSE
  rerun_fit_v2_surf: FALSE
  rerun_fit_v3_surf: FALSE
  rerun_fit_v4_surf: FALSE
  rerun_fit_v5_surf: FALSE
  rerun_simple_surf: FALSE
  rerun_model_surf: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.pos = "h"
)
```


```{r libraries}
library(here)
library(readxl)
library(janitor)
library(viridis)
library(zoo)
library(qwraps2)
library(knitr)
library(kableExtra)
library(lubridate)
library(RANN)
library(rstanarm)
library(bayesplot)
library(gridExtra)
library(grid)
library(lme4)
library(raster)
library(geostatsp)
library(tidyverse)
library(viridis)


source(here("analysis", "process-modis-data-function.R"))

seed_val <- 1423
set.seed(seed_val)
```


```{r read-process-data}
if (params$rerun_data) {
  ##### read-process-survey-data
  
  saliva_ELISA_log_shift <- 0.15
  
  sched_visit_names <- c(
    "VISIT 1 DENGUE INDEX",
    "VISIT 2  DENGUE INDEX",
    "VISIT 3 DENGUE INDEX",
    "VISIT 4 INDEX"
  )
  
  low_count_schools <- c( # schools with <= 5 study participants with saliva measurement
    "Amnor Antarak Cheat School",
    "Ampe Phnom",
    "Aphivodth", 
    "Christian School Khum Skus",
    "Kdey Amnor", 
    "Kindergarten Asian",
    "Kindergarten Kampuchea Asian",
    "Kindergarten Wattbor",
    "Kindergarten​ Salon",
    "Meatophoum School",
    "No Name",
    "Panha Bot School",
    "Phoumi Thmei",
    "Sinsisamuth"
  ) 
  
  
  aedes_survey_og <- read_excel(here("data", "pagodas_combined_data3.xlsx"))
  
  
  aedes_survey_cleaned <- aedes_survey_og %>% 
    clean_names() %>% 
    mutate(wet_season = ifelse(
      visit %in% c("VISIT 1 DENGUE INDEX", "VISIT 3 DENGUE INDEX"),
      yes = "yes",
      no = "no"
    )) %>% 
    mutate(visit_year = case_when(
      visit == "VISIT 1 DENGUE INDEX" ~ 0,
      visit %in% c("VISIT 2  DENGUE INDEX", "VISIT 3 DENGUE INDEX") ~ 1,
      visit == "VISIT 4 INDEX" ~ 2,
      TRUE ~ -99
    )) %>% 
    mutate(age = as.numeric(age)) %>% 
    mutate(age_cented3 = age - 3) %>%
    mutate(age_cented7 = age - 7) %>%
    mutate(age_cented = age - 6) %>%
    mutate(gender = factor(gender)) %>% 
    mutate(school_attended = str_to_title(school_attended)) %>% 
    mutate(specify_if_other = str_to_title(specify_if_other)) %>% 
    mutate(school_attended_all = ifelse(
      school_attended == "Other, Specify:",
      yes = specify_if_other,
      no = school_attended
    )) %>% 
    mutate(school_attended_all = factor(
      case_when(
        school_attended_all == "New Town" ~ "Kindergarten New Town",
        school_attended_all %in% c("Sin Si Sa Muth", "Sinsisamuth") ~ "Kindergarten Sin Si Sa Muth",
        school_attended_all == "Panha Bot" ~ "Panha Bot School",
        school_attended_all == "No Name" ~ "NA",
        TRUE ~ school_attended_all
      ))) %>% 
    mutate(school_attended_all = as.character(school_attended_all)) %>%
    mutate(in_school = factor(ifelse(
      school_attended_all != "Subject Not In School",
      yes = "yes",
      no = "no"
    ))) %>% 
    mutate(school_attended_red = factor(
      case_when(
        school_attended_all %in% low_count_schools ~ "other",
        TRUE ~ school_attended_all
      ),
      levels = c(
        "Subject Not In School",
        "Ang Seri",              
        "Anouvotta",             
        "Mroum Cheung",          
        "Mroum Tbaung",          
        "New Town",
        "Rkathom",
        "Santiphap",
        "Kindergarten Sin Si Sa Muth",
        "other"
      )
    )) %>% 
    select(-c("specify_if_other")) %>% 
    mutate(housing_type = factor(housing_type)) %>% 
    mutate(socioeconomic_class = factor(
      socioeconomic_class,
      levels = c("Very Poor", "Lower", "Middle", "Upper")
    )) %>% 
    mutate(visit_date = as.Date(visit_date)) %>% 
    mutate(sched_visit = ifelse(visit %in% sched_visit_names, yes = "yes", no = "no")) %>% 
    mutate(num_domestic_water_containers_in_home = as.numeric(num_domestic_water_containers_in_home)) %>% 
    mutate(num_toilets_in_home = as.numeric(num_toilets_in_home)) %>% 
    mutate(how_often_use_bed_net = factor(
      how_often_use_bed_net,
      levels = c(
        "Never", 
        "Rarely", 
        "Regularly/ Most of the time", 
        "All of the time"
      ),
      labels = c(
        "Never", 
        "Rarely", 
        "Most of the time", 
        "All of the time"
      )
    )) %>% 
    mutate(insecticide_spray = factor(insecticide_spray)) %>% 
    mutate(larvicide_applied_to_water = factor(larvicide_applied_to_water)) %>% 
    mutate(how_often_mosquito_coils_burned = factor(
      how_often_mosquito_coils_burned,
      levels = c(
        "Never", 
        "Rarely (about 1x/month)", 
        "Sometimes (about 1x/week)",
        "Often (about 3x/week)",
        "Daily"
      ),
      labels = c(
        "Never", 
        "~ 1x/month", 
        "~ 1x/week",
        "~ 3x/week",
        "Daily"
      )
    )) %>% 
    mutate(visit_date_abr = factor(as.yearmon(visit_date))) %>% 
    mutate(log_saliva_elisa = log(saliva_elisa_value + saliva_ELISA_log_shift)) 
  
  
  aedes_visit5 <- read_csv(here("data", "Saliva ELISA V1-6 INDEX.csv"), show_col_types = FALSE) %>% 
    select(study_id = ID, saliva_elisa_value = "Visit 5") %>% 
    mutate(saliva_elisa_value = as.numeric(ifelse(saliva_elisa_value == ".", yes = NA, no = saliva_elisa_value))) %>% 
    mutate(log_saliva_elisa = log(saliva_elisa_value + saliva_ELISA_log_shift)) 
    

  aedes_survey_cleaned_v1_v5 <- aedes_survey_cleaned[!duplicated(aedes_survey_cleaned$study_id), ] %>% 
      mutate(visit = "Visit 5") %>% 
      mutate(visit_date = as.Date("2020-07-01")) %>% 
      mutate(visit_date_abr = NA) %>% 
      mutate(wet_season = "yes") %>% 
      mutate(visit_year = 2) %>% 
      select(-c(saliva_elisa_value, log_saliva_elisa)) %>% 
      full_join(aedes_visit5) %>% 
      select(colnames(aedes_survey_cleaned)) %>% 
      bind_rows(aedes_survey_cleaned) %>% 
      arrange(study_id, visit_date)
  
  
  aedes_coord_og <- read_csv(here("data", "PAGODAS_Coordinates.csv"), show_col_types = FALSE)
  
  aedes_coord_cleaned <- aedes_coord_og %>%
    clean_names()
  
  aedes_full <- full_join(aedes_survey_cleaned_v1_v5, aedes_coord_cleaned) %>% 
    filter(sched_visit == "yes") %>% 
    mutate(visit = case_when(
      visit == "VISIT 1 DENGUE INDEX" ~ "visit1",
      visit == "VISIT 2  DENGUE INDEX" ~ "visit2",
      visit == "VISIT 3 DENGUE INDEX" ~ "visit3",
      visit == "VISIT 4 INDEX" ~ "visit4",
      visit == "Visit 5" ~ "visit5",
      TRUE ~ "NA"
    ))

  aedes_survey_with_river <- read_csv(here("data", "DistPHHtoRiver.csv"), show_col_types = FALSE) %>% 
    select(study_id = Study.ID, distance_to_river = distance) %>%
    mutate(distance_to_river_scaled = (distance_to_river - mean(distance_to_river)) / sd(distance_to_river)) %>% 
    mutate(close_to_river = factor(
      ifelse(distance_to_river <= params$near_river_cut_off, "yes", "no"), 
      levels = c("no", "yes")
    )) %>% 
    right_join(aedes_full)
  
  
  aedes_red <- aedes_survey_with_river %>% 
    filter(!is.na(saliva_elisa_value)) %>% 
    filter(!is.na(visit_date)) %>% 
    filter(school_attended_all != "NA") %>% 
    mutate(num_domestic_water_containers_in_home = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = num_domestic_water_containers_in_home
    )) %>% 
    mutate(num_toilets_in_home = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = num_toilets_in_home
    )) %>% 
    mutate(how_often_use_bed_net = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(how_often_use_bed_net)
    )) %>% 
    mutate(insecticide_spray = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(insecticide_spray)
    )) %>%
    mutate(larvicide_applied_to_water = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(larvicide_applied_to_water)
    )) %>%
    mutate(how_often_mosquito_coils_burned = ifelse(
      visit != "visit1", 
      yes = NA, 
      no = as.character(how_often_mosquito_coils_burned)
    ))

  
  time_varying <- read_xlsx(here("data", "AllVisitDataWithScheDengueRiskFactors.xlsx")) %>% 
    select(
      study_id = "Study ID", 
      visit = "Event Name",
      num_domestic_water_containers_in_home = "1. How many domestic water containers are in the subject's home?",
      num_toilets_in_home = "2. How many toilets are in the subject's home?",
      how_often_use_bed_net = "3. How often does the subject use a bed net?",
      insecticide_spray = "4. Is the subject's home sprayed with insecticide?",
      larvicide_applied_to_water = "5. Is larvicide applied to water containers at the subject's home?",
      how_often_mosquito_coils_burned = "6. How often are mosquito coils burned in the subject's house?",
    ) %>% 
    mutate(visit = gsub(" ", "", str_to_lower(visit), fixed = TRUE)) %>%
    filter(visit != "visit6") %>% 
    filter(!(study_id == "100-0468" & visit == "visit4")) %>% # Missing data
    mutate(num_domestic_water_containers_in_home = as.numeric(num_domestic_water_containers_in_home)) %>% 
    mutate(num_toilets_in_home = as.numeric(num_toilets_in_home)) %>% 
    mutate(how_often_use_bed_net = as.character(factor(
      how_often_use_bed_net,
      levels = c(
        "Never", 
        "Rarely", 
        "Regularly/ Most of the time", 
        "All the time"
      ),
      labels = c(
        "Never", 
        "Rarely", 
        "Most of the time", 
        "All of the time"
      )
    ))) %>% 
    mutate(how_often_mosquito_coils_burned = as.character(factor(
      how_often_mosquito_coils_burned,
      levels = c(
        "Never", 
        "Rarely (about 1x/month)", 
        "Sometimes (about 1x/week)",
        "Often (about 3x/week)",
        "Daily"
      ),
      labels = c(
        "Never", 
        "~ 1x/month", 
        "~ 1x/week",
        "~ 3x/week",
        "Daily"
      )
    )))
  
  time_varying_vars <- c("num_domestic_water_containers_in_home", "num_toilets_in_home", "how_often_use_bed_net", "insecticide_spray", "larvicide_applied_to_water", "how_often_mosquito_coils_burned")
  
  
  aedes_red <- aedes_red %>% 
    filter(visit != "visit1") %>% 
    select(-time_varying_vars) %>% 
    left_join(time_varying) %>% 
    select(colnames(aedes_red)) %>% 
    bind_rows(aedes_red %>% filter(visit == "visit1")) %>% 
    mutate(visit = factor(visit)) %>% 
    mutate(visit5 = factor(ifelse(visit != "visit5", "no", "yes"))) %>% 
    mutate(wet_season = factor(wet_season, levels = c("no", "yes"))) %>% 
    filter(!is.na(num_domestic_water_containers_in_home)) %>% 
    mutate(how_often_use_bed_net = factor(
      how_often_use_bed_net,
      levels = c(
        "Never", 
        "Rarely", 
        "Most of the time", 
        "All of the time"
      )
    )) %>% 
    mutate(insecticide_spray = factor(insecticide_spray)) %>% 
    mutate(larvicide_applied_to_water = factor(larvicide_applied_to_water)) %>% 
    mutate(how_often_mosquito_coils_burned = factor(
      how_often_mosquito_coils_burned,
      levels = c(
        "Never", 
        "~ 1x/month", 
        "~ 1x/week",
        "~ 3x/week",
        "Daily"
      )
    ))
  
  
  aedes_red <- read_csv(here("data", "PAGODAS_Landtype.csv")) %>% 
    select(-c(X, Y, lon, lat, elevation)) %>% 
    clean_names() %>% 
    mutate(modal_land_type = factor(
      str_to_lower(modal_land_type), 
      levels = c("urban", "rice paddy", "cropland")
    )) %>% 
    right_join(aedes_red, by = "study_id")
  
  
  #### Incorporate satellite data
  max_date_diff <- 60
  date_lag <- params$modis_lag
  
  
  sat_data500 <- process_modis_data(
    df_og = read_csv(here("data", "MODIS_500m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 7
  ) %>% 
    arrange(Study.ID, var_type, date)
  
  
  sat_df <- sat_data500
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    df_id <- sat_df %>% 
      filter(Study.ID == as.character(df_og[i, "study_id"]))
    
    for(j in 1:num_vars) {
      df_id_var <- df_id %>% 
        filter(var_type == var_types[j])
      
      if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
        date_diff <- (df_og$visit_date[i] - days(date_lag)) - df_id_var$date
        curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
        
        if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
          print(paste0(
            "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
            var_types[j], " value available within ", max_date_diff, 
            " days [max_date_diff] of ", date_lag, " days [date_lag] prior to visit date!"
          ))
        } else {
          df_new[i, var_types[j]] <- curr$sat_var_value
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI500_home = EVI, NVI500_home = NVI, NFI500_home = NFI)
  
  
  #### Incorporate satellite data 
  sat_data250 <- process_modis_data(
    df_og = read_csv(here("data", "MODIS_250m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 7
  )
  
  
  sat_df <- sat_data250
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    df_id <- sat_df %>% 
      filter(Study.ID == as.character(df_og[i, "study_id"]))
    
    for(j in 1:num_vars) {
      df_id_var <- df_id %>% 
        filter(var_type == var_types[j])
      
      if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
        date_diff <- (df_og$visit_date[i] - days(date_lag)) - df_id_var$date
        curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
        
        if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
          print(paste0(
            "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
            var_types[j], " value available within ", max_date_diff, 
            " days [max_date_diff] of ", date_lag, " days [date_lag] prior to visit date!"
          ))
        } else {
          df_new[i, var_types[j]] <- curr$sat_var_value
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI250_home = EVI, NVI250_home = NVI, NFI250_home = NFI)
  
  
  #### Incorporate school satellite data 
  sat_data250 <- process_modis_data(
    df_og = read_csv(here("data", "SchoolsMODIS_250m.csv"), show_col_types = FALSE), 
    sat_var_names = c("EVI", "NVI", "NFI"), # keep order that it appear in df
    sat_var_col_start = 6
  ) %>% 
    mutate(names = ifelse(
      names == "Kindergarten<U+200B> Salon", 
      yes = "Kindergarten​ Salon", 
      no = names
    ))
  
  
  sat_df <- sat_data250
  df_og <- aedes_red
  df_new <- cbind(
    df_og, 
    "EVI" = rep(NA, nrow(df_og)),
    "NFI" = rep(NA, nrow(df_og)),
    "NVI" = rep(NA, nrow(df_og))
  )
  
  num_vars <- 3
  var_types <- levels(factor(sat_df$var_type))
  
  
  for(i in 1:nrow(df_og)) {
    if(df_og[i, "school_attended_all"] != "Subject Not In School") {
      df_id <- sat_df %>% 
        filter(names == as.character(df_og[i, "school_attended_all"]))
      
      for(j in 1:num_vars) {
        df_id_var <- df_id %>% 
          filter(var_type == var_types[j])
        
        if (sum(!is.na(df_id_var$sat_var_value)) > 0) {
          date_diff <- (df_og$visit_date[i] - days(date_lag)) - df_id_var$date
          curr <- df_id_var[which.min(ifelse(date_diff < 0, 1000, date_diff)), ]
          
          if (abs(curr$date - df_og$visit_date[i]) > max_date_diff) {
            print(paste0(
              "Warning: Study ID ", df_og[i, "study_id"], " does not have ", 
              var_types[j], " value available within ", max_date_diff, 
              " days [max_date_diff] of ", date_lag, " days [date_lag] prior to visit date!"
            ))
          } else {
            df_new[i, var_types[j]] <- curr$sat_var_value
          }
        }
      }
    }
  }
  
  aedes_red <- df_new %>% 
    rename(EVI250_sch = EVI, NVI250_sch = NVI, NFI250_sch = NFI) %>% 
    mutate(EVI250_sch = ifelse(is.na(EVI250_sch), yes = 0, no = EVI250_sch)) %>% 
    mutate(NVI250_sch = ifelse(is.na(NVI250_sch), yes = 0, no = NVI250_sch)) %>% 
    mutate(NFI250_sch = ifelse(is.na(NFI250_sch), yes = 0, no = NFI250_sch))                 
  
  aedes_red <- aedes_red[!is.na(aedes_red$NVI250_home), ]
  
  
  #### Incorporate larval data
  larval_lat_lo <- read_csv(here("data", "HH_Surveys_19Jan_UTM48N.csv"), show_col_types = FALSE) %>% 
    select(
      X = "X...1",
      Y = "Y...2",
      larval_lon = "X...3",
      larval_lat = "Y...4",
      house_num = "name",
      subj_id = "SUBJID"
    ) %>% 
    mutate(subj_id = as.character(as.numeric(subj_id))) %>% 
    filter(!duplicated(subj_id)) #subjects 389 and 716 had repeat measurements; 1st kept
    
  
  larval_hs <- read_xlsx(here("data", "House Survey Data_Extracted 03May2021.xlsx")) %>% 
    select(
      subj_id = SUBJID,
      larval_visit_date = VISITDAT,
      water_containers = WATERCON,
      water_larvae = WATERLARVAE
    ) %>% 
    filter(water_containers > 0) %>% 
    mutate(subj_id = as.character(subj_id)) %>% 
    mutate(container_index = as.numeric(water_larvae) / as.numeric(water_containers)) %>% 
    left_join(y = larval_lat_lo) 
  
  larval_nn <- nn2(
    select(.data = larval_hs, larval_lon, larval_lat),
    query = select(.data = aedes_red, lon, lat), 
    k = 1,
    radius = 300
  )
  
  aedes_red <- aedes_red %>% 
    mutate(larvae_cont_ind = larval_hs$container_index[larval_nn$nn.idx])
  
  
  saveRDS(aedes_red, file = here("data", "processed_aedes_data.rds"))
  
} else { 
  aedes_red <- readRDS(file = here("data", "processed_aedes_data.rds")) 
}
  

aedes_red <- aedes_red %>% 
  mutate(lat_s = (lat - mean(lat)) / sd(lat)) %>% 
  mutate(lon_s = (lon - mean(lon)) / sd(lon))

aedes_red_ind <- aedes_red %>%
  filter(visit == "visit1") %>% 
  mutate(visit = droplevels(visit))
```


```{r visit_measurement_counts}
summary(aedes_red$visit)
```

\newpage
## EDA table

```{r eda_tab, eval = FALSE}
aedes_summary <- list(
  "Age" = list(
    "min" = ~ min(age),
    "mean (sd)" = ~ mean_sd(age),
    "max" = ~ max(age)
  ),
  "Gender" = list(
    "Male" = ~ n_perc0(gender == "Female"),
    "Female" = ~ n_perc0(gender == "Male")
  ),
  "School attended" = list(
    "Ampe phnom" = ~ n_perc0(school_attended == "Ampe phnom"),
    "Ang seri" = ~ n_perc0(school_attended == "Ang seri"),
    "Anouvotta" = ~ n_perc0(school_attended == "Anouvotta"),
    "Aphivodth" = ~ n_perc0(school_attended == "Aphivodth"),
    "Mroum cheung" = ~ n_perc0(school_attended == "Mroum cheung"),
    "Mroum tbaung" = ~ n_perc0(school_attended == "Mroum tbaung"),
    "Phoumi thmei" = ~ n_perc0(school_attended == "Phoumi thmei"),
    "Rkathom" = ~ n_perc0(school_attended == "Rkathom"),
    "Santiphap" = ~ n_perc0(school_attended == "Santiphap"),
    "Other" = ~ n_perc0(school_attended == "Other, specify:"),
    "Not in school" = ~ n_perc0(school_attended == "Subject not in school")
  ),
  "Socioeconomic class" = list(
    "Lower" = ~ n_perc0(socioeconomic_class == "Lower"),
    "Middle" = ~ n_perc0(socioeconomic_class == "Middle"),
    "Upper" = ~ n_perc0(socioeconomic_class == "Upper"),
    "Very Poor" = ~ n_perc0(socioeconomic_class == "Very Poor")
  ),
  "Domestic water containers" = list(
    "min" = ~ min(num_domestic_water_containers_in_home),
    "mean (sd)" = ~ mean_sd(num_domestic_water_containers_in_home),
    "max" = ~ max(num_domestic_water_containers_in_home)
  ),
  "Number toilets in home" = list(
    "min" = ~ min(num_toilets_in_home),
    "mean (sd)" = ~ mean_sd(num_toilets_in_home),
    "max" = ~ max(num_toilets_in_home)
  ),
  "Bed net use" = list(
    "Never" = ~ n_perc0(how_often_use_bed_net == "Never"),
    "Rarely" = ~ n_perc0(how_often_use_bed_net == "Rarely"),
    "Regularly/ Most of the time" = ~ n_perc0(how_often_use_bed_net == "Regularly/ Most of the time"),
    "All of the time" = ~ n_perc0(how_often_use_bed_net == "All of the time")
  ),
  "Insecticide spray" = list(
    "No" = ~ n_perc0(insecticide_spray == "No"),
    "Yes" = ~ n_perc0(insecticide_spray == "Yes")
  ),
  "Larvicide applied to water" = list(
    "No" = ~ n_perc0(larvicide_applied_to_water == "No"),
    "Yes" = ~ n_perc0(larvicide_applied_to_water == "Yes")
  ),
  "Mosquito coils burned" = list(
    "Never" = ~ n_perc0(how_often_mosquito_coils_burned == "Never"),
    "Rarely (about 1x/month)" = ~ n_perc0(how_often_mosquito_coils_burned == "Rarely (about 1x/month)"),
    "Sometimes (about 1x/week)" = ~ n_perc0(how_often_mosquito_coils_burned == "Sometimes (about 1x/week)"),
    "Often (about 3x/week)" = ~ n_perc0(how_often_mosquito_coils_burned == "Often (about 3x/week)"),
    "Daily" = ~ n_perc0(how_often_mosquito_coils_burned == "Daily")
  )
)

aedes_summary_tab <- summary_table(aedes_red_ind, aedes_summary)

kable(aedes_summary_tab) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  group_rows(group_label = "Age", start_row = 1, end_row = 3) %>% 
  group_rows(group_label = "Gender", 4, 5) %>% 
  group_rows(group_label = "School attended", 6, 16) %>% 
  group_rows(group_label = "Socioeconomic level", 17, 20) %>% 
  group_rows(group_label = "Domestic water containers", 21, 23) %>% 
  group_rows(group_label = "Number toilets in home", 24, 26) %>% 
  group_rows(group_label = "Bed net use", 27, 30) %>% 
  group_rows(group_label = "Insecticide spray", 31, 32) %>% 
  group_rows(group_label = "Larvicide applied to water", 33, 34) %>% 
  group_rows(group_label = "Mosquito coils burned", 35, 39)
```

\newpage

```{r saliva-elisa-mapped, fig.dim=c(8,8.25)}
aedes_red %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = saliva_elisa_value)) +
    geom_point(alpha = 0.75) +
    scale_color_viridis(direction = -1) +
    theme_bw() +
    lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
    coord_equal(ratio = 1) +
    facet_wrap(~ visit) +
    theme(legend.position="bottom")
```

\newpage

```{r saliva-elisa-mapped-extreme-dropped, fig.dim=c(8,8.25)}
aedes_red %>% 
  filter(study_id != "100-0022") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = saliva_elisa_value)) +
    geom_point(alpha = 0.75) +
    scale_color_viridis(direction = -1) +
    theme_bw() +
    lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
    coord_equal(ratio = 1) +
    facet_wrap(~ visit) +
    theme(legend.position="bottom")
```

\newpage

```{r elisa-by-visit, fig.asp=0.7}
aedes_red %>% 
  ggplot(mapping = aes(x = visit, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw()
```


```{r elisa-by-visit_date, fig.asp=0.7}
aedes_red %>% 
  ggplot(mapping = aes(x = visit_date, y = saliva_elisa_value)) +
    geom_point() +
    theme_bw() +
    ggtitle("Saliva ELISA value by visit data")
```

\newpage

```{r elisa-by-elevation, fig.asp=0.7}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = elevation, y = saliva_elisa_value)) +
    geom_point() +
  theme_bw()
```


```{r elevation-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = elevation)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```


\newpage

## Plots of saliva ELISA value by predictors

```{r elisa-by-age, fig.asp=0.6}
aedes_red_ind %>% 
  mutate(age = factor(age)) %>% 
  ggplot(mapping = aes(x = age, y = saliva_elisa_value)) +
  geom_boxplot() +
  theme_bw()
```


```{r age-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  mutate(age = factor(age)) %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = age)) +
  geom_point() +
  scale_color_viridis(discrete = TRUE, direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-gender, fig.asp=0.7}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = gender, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw()
```


```{r gender-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = gender, shape = gender)) +
  geom_point(alpha = 0.75) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-school_attended, fig.asp=0.7}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = school_attended, y = saliva_elisa_value)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))
```


```{r school_attended-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = school_attended)) +
  geom_point(alpha = 0.75) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-num_domestic_water_containers_in_home, fig.asp=0.7}
aedes_red_ind %>% 
  mutate(num_domestic_water_containers_in_home = factor(num_domestic_water_containers_in_home)) %>% 
  ggplot(mapping = aes(x = num_domestic_water_containers_in_home, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw() +
  xlab("Number of domestic water containers in home") +
  ylab("Saliva ELISA value")
```


```{r num_domestic_water_containers_in_home-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  mutate(water_cont = num_domestic_water_containers_in_home) %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = water_cont)) +
  geom_point(alpha = 0.75) +
  theme_bw() +
  scale_color_viridis(direction = -1) +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-num_toilets_in_home, fig.asp=0.7}
aedes_red_ind %>% 
  mutate(num_toilets_in_home = factor(num_toilets_in_home)) %>% 
  ggplot(mapping = aes(x = num_toilets_in_home, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw() +
  xlab("Number of toilets in home") +
  ylab("Saliva ELISA value")
```


```{r num_toilets_in_home-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  mutate(toilets = num_toilets_in_home) %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = toilets)) +
  geom_point(alpha = 0.75) +
  theme_bw() +
  scale_color_viridis(direction = -1) +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-how_often_use_bed_net, fig.asp=0.7}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = how_often_use_bed_net, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw()
```


```{r how_often_use_bed_net-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  mutate(bed_net = how_often_use_bed_net) %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = bed_net)) +
  geom_point(alpha = 0.75) +
  theme_bw() +
  scale_color_viridis(direction = -1, discrete = TRUE) +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-insecticide_spray, fig.asp=0.7}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = insecticide_spray, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw() +
  xlab("Insecticide") +
  ylab("Saliva ELISA value")
```


```{r insecticide_spray-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  mutate(insecticide = insecticide_spray) %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = insecticide)) +
  geom_point(alpha = 0.75) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-larvicide_applied_to_water, fig.asp=0.7}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = larvicide_applied_to_water, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw() +
  xlab("Larvicide") +
  ylab("Saliva ELISA value")
```


```{r larvicide_applied_to_water-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  mutate(larvicide = larvicide_applied_to_water) %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = larvicide)) +
  geom_point(alpha = 0.75) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-how_often_mosquito_coils_burned, fig.asp=0.7}
aedes_red_ind %>% 
  ggplot(mapping = aes(x = how_often_mosquito_coils_burned, y = saliva_elisa_value)) +
    geom_boxplot() +
  theme_bw()
```


```{r how_often_mosquito_coils_burned-mapped, fig.asp=0.9}
aedes_red_ind %>% 
  mutate(coils = how_often_mosquito_coils_burned) %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = coils)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1, discrete = TRUE) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1)
```

\newpage

```{r elisa-by-EVI, fig.asp=0.7, eval = FALSE}
aedes_red %>% 
  ggplot(mapping = aes(x = EVI, y = saliva_elisa_value)) +
    geom_point() +
  theme_bw() +
  facet_wrap(~ visit)
```


```{r EVI-visit1-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit1") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = EVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 1")
```


```{r EVI-visit2-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit2") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = EVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 2")
```


```{r EVI-visit3-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit3") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = EVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 3")
```


```{r EVI-visit4-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit4") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = EVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 4")
```


```{r elisa-by-NFI, fig.asp=0.7, eval = FALSE}
aedes_red %>% 
  ggplot(mapping = aes(x = NFI, y = saliva_elisa_value)) +
    geom_point() +
  theme_bw() +
  facet_wrap(~ visit)
```


```{r NFI-visit1-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit1") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NFI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 1")
```


```{r NFI-visit2-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit2") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NFI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 2")
```


```{r NFI-visit3-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit3") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NFI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 3")
```


```{r NFI-visit4-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit4") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NFI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 4")
```

\newpage

```{r elisa-by-NVI, fig.asp=0.7, eval = FALSE}
aedes_red %>% 
  ggplot(mapping = aes(x = NVI, y = saliva_elisa_value)) +
    geom_point() +
  theme_bw() +
  facet_wrap(~ visit)
```


```{r NVI-visit1-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit1") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 1")
```


```{r NVI-visit2-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit2") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 2")
```


```{r NVI-visit3-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit3") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 3")
```


```{r NVI-visit4-mapped, fig.asp=0.9, eval = FALSE}
aedes_red %>% 
  filter(visit == "visit4") %>% 
  ggplot(mapping = aes(x = lon, y = lat, color = NVI)) +
  geom_point(alpha = 0.75) +
  scale_color_viridis(direction = -1) +
  theme_bw() +
  lims(x = c(104.50, 104.56), y = c(11.43, 11.49)) +
  coord_equal(ratio = 1) +
  ggtitle("Visit 4")
```




## Pairwise plots of predictors
```{r pariwise-plots-of-predictors, eval = FALSE}
library(GGally)

pdf(here("analysis", "preds-pair-plot.pdf"), width = 40, height = 30)

ggpairs(aedes_red_ind[, c(3:5, 8:14, 29, 36:39)])

dev.off()
```








\newpage

## Model 

```{r, eval = FALSE}
ggplot(aedes_red_ind, aes(x = saliva_elisa_value)) +
  geom_histogram()


ggplot(aedes_red, aes(x = log(saliva_elisa_value + 0.015))) +
  geom_histogram() +
  theme_bw()
```

Initial model for log saliva ELISA value of individual $i$ at measurement $j$ ($i=1,...,726$, $j=1,...,4$).
\begin{equation*}
	\begin{split}
		\log(\text{Saliva ELISA value})_{ij} &= b_{0_{i}} + \beta_{0} + \beta_{1}\text{Male}_i + \beta_{2-10}\text{School}_{i} \\
		&+ \beta_{11}(\text{Age} - 6)_{i} + \beta_{12}\text{Toilets}_{i} + \beta{13}\text{Water Containers}_i + \beta_{14}\text{Insecticide}_{i} + \beta_{15}\text{Larvicide}_{i} \\
		&+ \beta_{16}\text{NFI}_{ij} + \beta_{17}\text{NVI}_{ij} \\
		&+ \beta_{18}\text{Visit2}_{ij} + \beta_{19}\text{Visit3}_{ij} + \beta_{20}\text{Visit4}_{ij},
	\end{split}
\end{equation*}
with "subject not in school" as reference group for school covariate.

```{r fit1-bayes-NVI500}
if(params$rerun_fit1_bayes) {
  fit1_bayes <- stan_lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + num_domestic_water_containers_in_home + 
      insecticide_spray + larvicide_applied_to_water +
      NFI500_home + NVI500_home + visit,
    data = aedes_red,
    seed = seed_val
  )
  
  saveRDS(fit1_bayes, file = here("output", "fit1-bayes.rds"))
  
} else { 
  fit1_bayes <- readRDS(file = here("output", "fit1-bayes.rds")) 
}
```


```{r fit2-bayes-NVI250}
if(params$rerun_fit2_bayes) {
  fit2_bayes <- stan_lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + num_domestic_water_containers_in_home + 
      insecticide_spray + larvicide_applied_to_water +
      NFI250_home + NVI250_home + visit,
    data = aedes_red,
    seed = seed_val
  )
  
  saveRDS(fit2_bayes, file = here("output", "fit2-bayes.rds"))
  
} else { 
  fit2_bayes <- readRDS(file = here("output", "fit2-bayes.rds")) 
}
```


```{r fit3-bayes-EVI500}
if(params$rerun_fit3_bayes) {
  fit3_bayes <- stan_lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + num_domestic_water_containers_in_home +
      insecticide_spray + larvicide_applied_to_water +
      NFI500_home + EVI500_home + visit,
    data = aedes_red,
    seed = seed_val
  )
  
  saveRDS(fit3_bayes, file = here("output", "fit3-bayes.rds"))
  
} else { 
  fit3_bayes <- readRDS(file = here("output", "fit3-bayes.rds")) 
}
```


```{r fit4-bayes-EVI250}
if(params$rerun_fit4_bayes) {
  fit4_bayes <- stan_lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + num_domestic_water_containers_in_home +
      insecticide_spray + larvicide_applied_to_water +
      NFI250_home + EVI250_home + visit,
    data = aedes_red,
    seed = seed_val
  )
  
  saveRDS(fit4_bayes, file = here("output", "fit4-bayes.rds"))
  
} else { 
  fit4_bayes <- readRDS(file = here("output", "fit4-bayes.rds")) 
}
```

\blandscape

```{r gen_post_plots-function}
gen_post_plots <- function(fit){
  fit_post_area1 <- mcmc_areas(fit, regex_pars = "school",
    prob = 0.95, prob_outer = 0.99) +
    scale_y_discrete(labels = c(
      "school_attended_redAng Seri" = "Ang Seri",
      "school_attended_redAnouvotta" = "Anouvotta",
      "school_attended_redMroum Cheung" = "Mroum Cheung",
      "school_attended_redMroum Tbaung" = "Mroum Tbaung",
      "school_attended_redNew Town" = "New Town",
      "school_attended_redPanha Bot" = "Panha Bot",
      "school_attended_redRkathom" = "Rkathom",
      "school_attended_redSantiphap" = "Santiphap",
      "school_attended_redSin Si Sa Muth" = "Sin Si Sa Muth",
      "school_attended_redother" = "other"
    ))
  
  fit_post_area2 <- mcmc_areas(
    fit,
    regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide"),
    prob = 0.95, prob_outer = 0.99
  )
  
  fit_post_area3 <- mcmc_areas(fit, regex_pars = c("NFI", "NVI", "EVI"),
    prob = 0.95, prob_outer = 0.99)
  
  fit_post_area4 <- mcmc_areas(fit, regex_pars = c("visit"),
    prob = 0.95, prob_outer = 0.99) 
  
  grid.arrange(
    fit_post_area1, fit_post_area2, fit_post_area3, fit_post_area4, 
    nrow = 2
  )
}
```


Fit 1 (NVI500) Results
```{r fit1-bayes-results, fig.width=10, fig.height=7.5}
gen_post_plots(fit1_bayes)
```


\newpage

Fit 2 (NVI250) Results
```{r fit2-bayes-results, fig.width=10, fig.height=7.5}
gen_post_plots(fit2_bayes)
```

\newpage

Fit 3 (EVI500) Results
```{r fit3-bayes-results, fig.width=10, fig.height=7.5}
gen_post_plots(fit3_bayes)
```


\newpage

Fit 4 (EVI250) Results
```{r fit4-bayes-results, fig.width=10, fig.height=7.5}
gen_post_plots(fit4_bayes)
```

\elandscape


```{r trace-plots, eval = FALSE}
mcmc_trace(fit1_bayes, regex_pars = "school")
mcmc_trace(fit2_bayes, regex_pars = "school")
mcmc_trace(fit3_bayes, regex_pars = "school")
mcmc_trace(fit4_bayes, regex_pars = "school")

mcmc_trace(fit1_bayes, regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide"))
mcmc_trace(fit2_bayes, regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide"))
mcmc_trace(fit3_bayes, regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide"))
mcmc_trace(fit4_bayes, regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide"))

mcmc_trace(fit1_bayes, regex_pars = c("NFI", "NVI"))
mcmc_trace(fit2_bayes, regex_pars = c("NFI", "NVI"))
mcmc_trace(fit3_bayes, regex_pars = c("NFI", "EVI"))
mcmc_trace(fit4_bayes, regex_pars = c("NFI", "EVI"))

mcmc_trace(fit1_bayes, regex_pars = c("visit"))
mcmc_trace(fit2_bayes, regex_pars = c("visit"))
mcmc_trace(fit3_bayes, regex_pars = c("visit"))
mcmc_trace(fit4_bayes, regex_pars = c("visit"))
```


\newpage
## Frequentist fit
```{r fit1-freq-NVI500}
if(params$rerun_fit1_freq) {
  fit1_freq <- lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + insecticide_spray + larvicide_applied_to_water +
      NFI500_home + NVI500_home + visit,
    data = aedes_red
  )
  
  saveRDS(fit1_freq, file = here("output", "fit1-freq.rds"))
  
} else { 
  fit1_freq <- readRDS(file = here("output", "fit1-freq.rds")) 
}
```


```{r fit2-freq-NVI250}
if(params$rerun_fit2_freq) {
  fit2_freq <- lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + insecticide_spray + larvicide_applied_to_water +
      NFI250_home + NVI250_home + visit,
    data = aedes_red
  )
  
  saveRDS(fit2_freq, file = here("output", "fit2-freq.rds"))
  
} else { 
  fit2_freq <- readRDS(file = here("output", "fit2-freq.rds")) 
}
```


```{r fit3-freq-EVI500}
if(params$rerun_fit3_freq) {
  fit3_freq <- lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + insecticide_spray + larvicide_applied_to_water +
      NFI500_home + EVI500_home + visit,
    data = aedes_red
  )
  
  saveRDS(fit3_freq, file = here("output", "fit3-freq.rds"))
  
} else { 
  fit3_freq <- readRDS(file = here("output", "fit3-freq.rds")) 
}
```


```{r fit4-freq-EVI250}
if(params$rerun_fit1_freq) {
  fit4_freq <- lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + school_attended_red + 
      age_cented + num_toilets_in_home + insecticide_spray + larvicide_applied_to_water +
      NFI250_home + EVI250_home + visit,
    data = aedes_red
  )
  
  saveRDS(fit4_freq, file = here("output", "fit4-freq.rds"))
  
} else { 
  fit4_freq <- readRDS(file = here("output", "fit4-freq.rds")) 
}
```


```{r gen_res_plot-function}
gen_res_plot <- function(fit){
  fit_freq_sum <- summary(fit)
  coeffs <- data.frame(fit_freq_sum$coefficients)[-1, ]
  fit_res <- data.frame(
    pred = rownames(coeffs),
    "estimates" = coeffs$Estimate,
    "lb95" = coeffs$Estimate - qnorm(0.025) * coeffs$Std..Error,
    "up95" = coeffs$Estimate + qnorm(0.025) * coeffs$Std..Error
  )
  rownames(fit_res) <- rownames(coeffs)
  
  ggplot(fit_res, mapping = aes(x = estimates, y = pred)) +
    geom_point() +
    geom_linerange(aes(xmin = lb95, xmax = up95)) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    scale_y_discrete(limits = rev(fit_res$pred)) +
    theme_bw()
}
```


```{r fit1-freq-NVI500-results}
gen_res_plot(fit1_freq)
```


```{r fit2-freq-NVI250-results}
gen_res_plot(fit2_freq)
```


```{r fit3-freq-EVI500-results}
gen_res_plot(fit3_freq)
```


```{r fit3-freq-EVI250-results}
gen_res_plot(fit4_freq)
```



\newpage
## Updated model with school modis and 5 visits

Updated model for log saliva ELISA value of individual $i$ at measurement $j$ ($i=1,...,726$, $j=1,...,5$).


\begin{equation*}
	\begin{split}
		\log(\text{Saliva ELISA value})_{ij} &= b_{0i} + \beta_{0} + \beta_{1}\text{Male}_i \\
		&+ \beta_{2}(\text{Age} - 6)_{i} + \beta_{3}\text{Toilets}_{ij} + \beta{4}\text{Water Containers}_{ij} + \beta_{5}\text{Insecticide}_{ij} + \beta_{6}\text{Larvicide}_{ij} \\
		&+ \beta_{7}\text{NFI250 home}_{ij} + \beta_{8}\text{EVI250 home}_{ij} \\
		&+ \beta_{9}\text{NFI250 sch}_{ij} + \beta_{10}\text{EVI250 sch}_{ij} \\
		&+ \beta_{11}\text{Visit2}_{ij} + \beta_{12}\text{Visit3}_{ij} + \beta_{13}\text{Visit4}_{ij} + \beta_{14}\text{Visit5}_{ij},
	\end{split}
\end{equation*}


```{r fit5-bayes-EVI250}
if(params$rerun_fit5_bayes) {
  fit5_bayes <- stan_lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + 
      age_cented + num_toilets_in_home + num_domestic_water_containers_in_home + 
      insecticide_spray + larvicide_applied_to_water + in_school +
      NFI250_home + EVI250_home + NFI250_sch + EVI250_sch + visit,
    data = aedes_red,
    seed = seed_val
  )
  
  saveRDS(fit5_bayes, file = here("output", "fit5-bayes.rds"))
  
} else { 
  fit5_bayes <- readRDS(file = here("output", "fit5-bayes.rds")) 
}
```

\blandscape
Fit 5
```{r, fig.width=10, fig.height=7.5}
gen_post_plots <- function(fit){
  fit_post_area2 <- mcmc_areas(
    fit,
    regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide", "in_school"),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "genderMale" = "Sex(male)",
      "age_centered" = "Age",
      "num_toilets_in_home" = "Toilets",
      "num_domestic_water_containers_in_home" = "Water containers",
      "larvicide_applied_to_waterYes" = "Larviced(yes)",
      "insecticide_sprayYes" = "Insecticide(yes)",
      "in_schoolyes" = "In school"
    ))
  
  fit_post_area3 <- mcmc_areas(fit, regex_pars = c("NFI250_home", "NVI250_home", "EVI250_home"),
    prob = 0.95, prob_outer = 0.99) 
  
  fit_post_area1 <- mcmc_areas(fit, regex_pars = c("NFI250_sch", "NVI250_sch", "EVI250_sch"),
    prob = 0.95, prob_outer = 0.99)
  
  fit_post_area4 <- mcmc_areas(fit, regex_pars = c("visit"), prob = 0.95, prob_outer = 0.99) +
    scale_y_discrete(labels = c(
      "visitvisit2" = "visit2",
      "visitvisit3" = "visit3",
      "visitvisit4" = "visit4",
      "visitvisit5" = "visit5"
    ))
  
  grid.arrange(
    fit_post_area1, fit_post_area2, fit_post_area3, fit_post_area4, 
    nrow = 2
  )
}

gen_post_plots(fit5_bayes)
```

\elandscape

```{r, eval = FALSE}
mcmc_trace(fit5_bayes, regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide"))

mcmc_trace(fit5_bayes, regex_pars = c("NFI", "EVI"))

mcmc_trace(fit5_bayes, regex_pars = c("visit"))
```




```{r fit6-bayes-EVI250}
aedes_red_sch <- aedes_red[aedes_red$in_school == "yes",]

if(params$rerun_fit6_bayes) {
  fit6_bayes <- stan_lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + 
      age_cented + num_toilets_in_home + num_domestic_water_containers_in_home + 
      insecticide_spray + larvicide_applied_to_water + #in_school +
      NFI250_home + EVI250_home + NFI250_sch + EVI250_sch + visit,
    data = aedes_red_sch,
    seed = seed_val
  )
  
  saveRDS(fit6_bayes, file = here("output", "fit6-bayes.rds"))
  
} else { 
  fit6_bayes <- readRDS(file = here("output", "fit6-bayes.rds")) 
}


aedes_red_sch_no <- aedes_red[aedes_red$in_school == "no",]

if(params$rerun_fit7_bayes) {
  fit7_bayes <- stan_lmer(
    formula = log_saliva_elisa ~ (1 | study_id) + 1 + gender + 
      age_cented + num_toilets_in_home + num_domestic_water_containers_in_home + 
      insecticide_spray + larvicide_applied_to_water + #in_school +
      NFI250_home + EVI250_home + visit,
    data = aedes_red_sch_no,
    seed = seed_val
  )
  
  saveRDS(fit7_bayes, file = here("output", "fit7-bayes.rds"))
  
} else { 
  fit7_bayes <- readRDS(file = here("output", "fit7-bayes.rds")) 
}
```

\blandscape

Fit 6: only children in school
```{r, fig.width=10, fig.height=7.5}
gen_post_plots(fit6_bayes)
```

\newpage
Fit 7: only children not in school
```{r, fig.width=10, fig.height=7.5}
gen_post_plots <- function(fit){
  fit_post_area2 <- mcmc_areas(
    fit,
    regex_pars = c("gender", "age", "toilets", "water", "insecticide", "larvicide"),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "genderMale" = "Sex(male)",
      "age_centered" = "Age",
      "num_toilets_in_home" = "Toilets",
      "num_domestic_water_containers_in_home" = "Water containers",
      "larvicide_applied_to_waterYes" = "Larviced(yes)",
      "insecticide_sprayYes" = "Insecticide(yes)"
    ))
  
  fit_post_area3 <- mcmc_areas(fit, regex_pars = c("NFI250_home", "NVI250_home", "EVI250_home"),
    prob = 0.95, prob_outer = 0.99) 
  
  fit_post_area4 <- mcmc_areas(fit, regex_pars = c("visit"),
    prob = 0.95, prob_outer = 0.99) +
    scale_y_discrete(labels = c(
      "visitvisit2" = "visit2",
      "visitvisit3" = "visit3",
      "visitvisit4" = "visit4",
      "visitvisit5" = "visit5"
    ))
  
  grid.arrange(
    textGrob(" "), fit_post_area2, fit_post_area3, fit_post_area4, 
    nrow = 2
  )
}


gen_post_plots(fit7_bayes)
```


\elandscape


## Split Models (young and school)  

```{r}
gen_post_plots <- function(fit){
  fit_post_area1 <- mcmc_areas(
    fit,
    regex_pars = c("toilets", "water", "larvicide", "insecticide" , "season"),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "num_toilets_in_home" = "Toilets",
      "num_domestic_water_containers_in_home" = "Water containers",
      "larvicide_applied_to_waterYes" = "Larvicide(yes)",
      "insecticide_sprayYes" = "Insecticide(yes)",
      "wet_seasonyes" = "Wet Season(yes)"
    ))

  fit_post_area2 <- mcmc_areas(
    fit,
    regex_pars = c("gender", "age", "school", "river", "year"),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "genderMale" = "Sex(male)",
      "age_centered3" = "Age",
      "in_schoolyes" = "In School(yes)",
      "distance_to_river_scaled" = "Distance to river",
      "visit_year" = "Visit year"
    ))
  
  fit_post_area3 <- mcmc_areas(fit, regex_pars = c("EVI250_home"),
    prob = 0.95, prob_outer = 0.99)
  
  fit_post_area4 <- mcmc_areas(fit, regex_pars = c("NFI250_home"),
    prob = 0.95, prob_outer = 0.99)
  
  
  grid.arrange(
    fit_post_area1, fit_post_area2, fit_post_area3, fit_post_area4, 
    nrow = 2
  )
}
```


\newpage

Model fit: Young children without interactions  
Updated model for log saliva ELISA value of individual $i$ at measurement $j$ ($i=1,...,726$, $j=1,...,5$), for Cambodian children ages 2-4.
\begin{equation*}
	\begin{split}
		\log(\text{Saliva ELISA value})_{ij} &= b_{0i} + \beta_{0} + \beta_{\text{Male}}\text{Male}_i \\
		&+ \beta_{\text{Age}}(\text{Age} - 3)_{i} + \beta_{\text{School}}\text{Attends school}_{i} + \beta_{\text{River}}\text{Lives near river}_{i}\\
		&+\beta_{\text{Toilets}}\text{Toilets}_{ij} + \beta_{\text{Water}}\text{Water containers}_{ij} + \beta_{\text{Insecticide}}\text{Insecticide}_{ij} + \beta_{\text{Larvicide}}\text{Larvicide}_{ij} \\
		&+ \beta_{\text{NFI250 home}}\text{Home flooding}_{ij} + \beta_{\text{EVI250 home}}\text{Home vegetation}_{ij} \\
		&+ \beta_{\text{Wet season}}\text{Wet season}_{ij} + \beta_{\text{Year}}\text{Year}_{ij},
	\end{split}
\end{equation*}

```{r fit-young1-bayes}
aedes_red_young <- aedes_red[aedes_red$age <= 4,]

if(params$rerun_fit_young) {
  fit_young <- stan_gamm4(
    formula = log_saliva_elisa ~ gender + 
      age_cented3 + in_school  + distance_to_river_scaled +
      modal_land_type +
      num_toilets_in_home + num_domestic_water_containers_in_home +
      insecticide_spray + larvicide_applied_to_water +
      NFI250_home + EVI250_home +
      wet_season + visit_year +
      visit5 + s(lat_s, lon_s, bs = "tp"),
    random = ~ (1 | study_id),
    data = aedes_red_young,
    seed = seed_val, 
    iter = 4000, 
    prior = normal(
      location = c(rep(0, 14), 0.1),
      scale = c(rep(2.5, 14), 0.05)
    )
  )
  
  saveRDS(fit_young, file = here("output", "fit-young.rds"))
  
} else { 
  fit_young <- readRDS(file = here("output", "fit-young.rds")) 
}
```

\blandscape
Young model without interactions (with visit 5)
```{r, fig.width=10, fig.height=7.5}
gen_post_plots(fit_young)
```
\elandscape

Model fit: Young children without interactions  
Updated model for log saliva ELISA value of individual $i$ at measurement $j$ ($i=1,...,726$, $j=1,...,5$), for Cambodian children ages 2-4.
\begin{equation*}
	\begin{split}
		\log(\text{Saliva ELISA value})_{ij} &= b_{0i} + \beta_{0} + \beta_{\text{Male}}\text{Male}_i \\
		&+ \beta_{\text{Age}}(\text{Age} - 3)_{i} + \beta_{\text{School}}\text{Attends school}_{i} + \beta_{\text{River}}\text{Lives near river}_{i}\\
		&+\beta_{\text{Toilets}}\text{Toilets}_{ij} + \beta_{\text{Water}}\text{Water containers}_{ij} + \beta_{\text{Insecticide}}\text{Insecticide}_{ij} + \beta_{\text{Larvicide}}\text{Larvicide}_{ij} \\
		&+ \beta_{\text{NFI250 home}}\text{Home flooding}_{ij} + \beta_{\text{EVI250 home}}\text{Home vegetation}_{ij} \\
		&+ \beta_{\text{Wet season}}\text{Wet season}_{ij} + \beta_{\text{Year}}\text{Year}_{ij},
	\end{split}
\end{equation*}

\newpage

Fit :  
Updated model for log saliva ELISA value of individual $i$ at measurement $j$ ($i=1,...,726$, $j=1,...,5$), for Cambodian school children (all ages).
\begin{equation*}
	\begin{split}
		\log(\text{Saliva ELISA value})_{ij} &= b_{0i} + \beta_{0} + \beta_{\text{Male}}\text{Male}_i \\
		&+ \beta_{\text{Age}}(\text{Age} - 7)_{i} + \beta_{\text{River}}\text{Lives near river}_{i}\\
		&+\beta_{\text{Toilets}}\text{Toilets}_{ij} + \beta_{\text{Water}}\text{Water containers}_{ij} + \beta_{\text{Insecticide}}\text{Insecticide}_{ij} + \beta_{\text{Larvicide}}\text{Larvicide}_{ij} \\
		&+ \beta_{\text{NFI250 home}}\text{Home flooding}_{ij} + \beta_{\text{EVI250 home}}\text{Home vegetation}_{ij} \\
		&+ \beta_{\text{NFI250 school}}\text{School school}_{ij} + \beta_{\text{EVI250 school}}\text{School vegetation}_{ij} \\
		&+ \beta_{\text{Wet season}}\text{Wet season}_{ij} + \beta_{\text{Year}}\text{Year}_{ij},
	\end{split}
\end{equation*}

```{r}
gen_post_plots <- function(fit){
  fit_post_area1 <- mcmc_areas(
    fit, 
    pars = c(
      "num_toilets_in_home",
      "num_domestic_water_containers_in_home",
      "larvicide_applied_to_waterYes",
      "insecticide_sprayYes",
      "wet_seasonyes"
    ),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "num_toilets_in_home" = "Toilets",
      "num_domestic_water_containers_in_home" = "Water containers",
      "larvicide_applied_to_waterYes" = "Larvicide(yes)",
      "insecticide_sprayYes" = "Insecticide(yes)",
      "wet_seasonyes" = "Wet Season(yes)"
    ))

  fit_post_area2 <- mcmc_areas(
    fit,
    regex_pars = c("gender", "age", "river", "year"),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "genderMale" = "Sex(male)",
      "age_centered3" = "Age",
      "distance_to_river_scaled" = "Distance to river",
      "visit_year" = "Visit year"
    ))
  
  fit_post_area3 <- mcmc_areas(fit, regex_pars = c("EVI"),prob = 0.95, prob_outer = 0.99)
  
  fit_post_area4 <- mcmc_areas(fit, regex_pars = c("NFI250"),
    prob = 0.95, prob_outer = 0.99)
  
  grid.arrange(
    fit_post_area1, fit_post_area2, fit_post_area3, fit_post_area4, 
    nrow = 2
  )
}
```


```{r fit-school}
aedes_red_school <- aedes_red[aedes_red$in_school == "yes",]

if(params$rerun_fit_school) {
  fit_school <- stan_gamm4(
    formula = log_saliva_elisa ~ gender + 
      age_cented7  + distance_to_river_scaled +
      modal_land_type +
      num_toilets_in_home + num_domestic_water_containers_in_home +
      insecticide_spray + larvicide_applied_to_water +
      NFI250_home + EVI250_home +
      NFI250_sch + EVI250_sch +
      wet_season + visit_year +
      visit5 + s(lat_s, lon_s, bs = "tp"),
    random = ~ (1 | study_id),
    data = aedes_red_school,
    seed = seed_val, 
    iter = 4000, 
    prior = normal(
      location = c(rep(0, 15), 0.1),
      scale = c(rep(2.5, 15), 0.05)
    )
  )
  
  saveRDS(fit_school, file = here("output", "fit-school.rds"))
  
} else { 
  fit_school <- readRDS(file = here("output", "fit-school.rds")) 
}
```

\blandscape
School model without interactions (with visit 5)
```{r, fig.width=10, fig.height=7.5}
gen_post_plots(fit_school)
```
\elandscape


## Main model without school predictors

Model for log saliva ELISA value of individual $i$ at measurement $j$ ($i=1,...,726$, $j=1,...,5$).
\begin{equation*}
	\begin{split}
		\log(\text{Saliva ELISA value})_{ij} &= b_{0i} + \beta_{0} + \beta_{\text{Male}}\text{Male}_i \\
		&+ \beta_{\text{Age}}(\text{Age} - 7)_{i} + \beta_{\text{River}}\text{Distance to river}_{i}\\
		&+\beta_{\text{Toilets}}\text{Toilets}_{ij} + \beta_{\text{Water}}\text{Water containers}_{ij} + \beta_{\text{Insecticide}}\text{Insecticide}_{ij} + \beta_{\text{Larvicide}}\text{Larvicide}_{ij} \\
		&+ \beta_{\text{NFI250 home}}\text{Home flooding}_{ij} + \beta_{\text{EVI250 home}}\text{Home vegetation}_{ij} \\
		&+ \beta_{\text{Wet season}}\text{Wet season}_{ij} + \beta_{\text{Year}}\text{Year}_{ij} + \beta_{\text{Larvae \%}}\text{Larvae \%}_{i},
	\end{split}
\end{equation*}

```{r gen-post-plots-for-main-model}
gen_post_plots <- function(fit){
  fit_post_area1 <- mcmc_areas(
    fit, 
    pars = c(
      "num_toilets_in_home",
      "num_domestic_water_containers_in_home",
      "larvicide_applied_to_waterYes",
      "insecticide_sprayYes"
    ),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "num_toilets_in_home" = "Toilets",
      "num_domestic_water_containers_in_home" = "Water containers",
      "larvicide_applied_to_waterYes" = "Larvicide(yes)",
      "insecticide_sprayYes" = "Insecticide(yes)"
    ))

  fit_post_area2 <- mcmc_areas(
    fit,
    regex_pars = c("gender", "age", "season", "visit_year"),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "genderMale" = "Sex(male)",
      "age_centered3" = "Age",
      "wet_seasonyes" = "Wet Season(yes)",
      "visit_year" = "Visit year"
    ))
  
  fit_post_area3 <- 
  
  fit_post_area4 <- mcmc_areas(
    fit, regex_pars = c("NFI250", "EVI250", "river"),
    prob = 0.95, prob_outer = 0.99
  ) +
    scale_y_discrete(labels = c(
      "distance_to_river_scaled" = "Distance to river"
    ))
  
  grid.arrange(
    fit_post_area1, fit_post_area2, fit_post_area4, 
    nrow = 2
  )
}
```


```{r fit-main1}
if(params$fit_main) {
  fit_main <- stan_gamm4(
    formula = log_saliva_elisa ~ gender + 
      age_cented7  + distance_to_river_scaled +
      modal_land_type +
      num_toilets_in_home + num_domestic_water_containers_in_home +
      insecticide_spray + larvicide_applied_to_water  +
      NFI250_home + EVI250_home +
      wet_season + visit_year +
      visit5 + s(lat_s, lon_s, bs = "tp"),
    random = ~ (1 | study_id),
    data = aedes_red,
    seed = seed_val, 
    iter = 4000, 
    prior = normal(
      location = c(rep(0, 13), 0.1),
      scale = c(rep(2.5, 13), 0.05)
    )
  )
  
  saveRDS(fit_main, file = here("output", "fit-main.rds"))
  
} else { 
  fit_main <- readRDS(file = here("output", "fit-main.rds")) 
}
```


```{r main-model-trace-plots, eval = FALSE}
mcmc_trace(fit_main, regex_pars = c("gender", "age", "river", "toilets"))

mcmc_trace(fit_main, regex_pars = c("water", "insecticide", "larvicide", "larvae"))

mcmc_trace(fit_main, regex_pars = c("NFI", "EVI"))

mcmc_trace(fit_main, regex_pars = c("season", "visit"))
```

\blandscape
```{r main-model-results, fig.width=10, fig.height=7.5}
gen_post_plots(fit_main)
```

```{r main-model-interaction-results}
plot_nonlinear(fit_main, prob = 0.95)+
  scale_color_viridis()
```


\elandscape


## Individual exposure surfaces

```{r visit1-exposure-surface}
if(params$rerun_fit_v1_surf){
  aedes_v1 <- filter(aedes_red, visit == "visit1")
  
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_v1, x = lon, y = lat),
    data = select(aedes_v1, log_saliva_elisa)
  )
  
  fit_v1_surf <- glgm(
    formula = log_saliva_elisa ~ 1,
    data = spdf,
    grid = 75
  )
  
  saveRDS(fit_v1_surf, here("output/map-models", "fit_v1_surf.rds"))
} else {
  fit_v1_surf <- readRDS(here("output/map-models", "fit_v1_surf.rds"))
}
```

```{r visit2-exposure-surface}
if(params$rerun_fit_v2_surf){
  aedes_v2 <- filter(aedes_red, visit == "visit2")
  
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_v2, x = lon, y = lat),
    data = select(aedes_v2, log_saliva_elisa)
  )
  
  fit_v2_surf <- glgm(
    formula = log_saliva_elisa ~ 1,
    data = spdf,
    grid = 75,
  )
  
  saveRDS(fit_v2_surf, here("output/map-models", "fit_v2_surf.rds"))
} else {
  fit_v2_surf <- readRDS(here("output/map-models", "fit_v2_surf.rds"))
}
```

```{r visit3-exposure-surface}
if(params$rerun_fit_v3_surf){
  aedes_v3 <- filter(aedes_red, visit == "visit3")
  
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_v3, x = lon, y = lat),
    data = select(aedes_v3, log_saliva_elisa)
  )
  
  fit_v3_surf <- glgm(
    formula = log_saliva_elisa ~ 1,
    data = spdf,
    grid = 75
  )
  
  saveRDS(fit_v3_surf, here("output/map-models", "fit_v3_surf.rds"))
} else {
  fit_v3_surf <- readRDS(here("output/map-models", "fit_v3_surf.rds"))
}
```

```{r visit4-exposure-surface}
if(params$rerun_fit_v4_surf){
  aedes_v4 <- filter(aedes_red, visit == "visit4")
  
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_v4, x = lon, y = lat),
    data = select(aedes_v4, log_saliva_elisa)
  )
  
  fit_v4_surf <- glgm(
    formula = log_saliva_elisa ~ 1,
    data = spdf,
    grid = 75
  )
  
  saveRDS(fit_v4_surf, here("output/map-models", "fit_v4_surf.rds"))
} else {
  fit_v4_surf <- readRDS(here("output/map-models", "fit_v4_surf.rds"))
}
```

```{r visit5-exposure-surface}
if(params$rerun_fit_v5_surf){
  aedes_v5 <- filter(aedes_red, visit == "visit5")
  
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_v5, x = lon, y = lat),
    data = select(aedes_v5, log_saliva_elisa)
  )
  
  fit_v5_surf <- glgm(
    formula = log_saliva_elisa ~ 1,
    data = spdf,
    grid = 75
  )
  
  saveRDS(fit_v5_surf, here("output/map-models", "fit_v5_surf.rds"))
} else {
  fit_v5_surf <- readRDS(here("output/map-models", "fit_v5_surf.rds"))
}
```

```{r display-visit-exposure-surface}
fit_visit_surfs <- bind_rows(
  as.data.frame(fit_v1_surf$raster$predict.mean, xy = TRUE) %>% 
  mutate(visit = "Visit 1"),
  as.data.frame(fit_v2_surf$raster$predict.mean, xy = TRUE) %>% 
  mutate(visit = "Visit 2"),
  as.data.frame(fit_v3_surf$raster$predict.mean, xy = TRUE) %>% 
  mutate(visit = "Visit 3"),
  as.data.frame(fit_v4_surf$raster$predict.mean, xy = TRUE) %>% 
  mutate(visit = "Visit 4"),
  as.data.frame(fit_v5_surf$raster$predict.mean, xy = TRUE) %>% 
  mutate(visit = "Visit 5")
)


ggplot() +
  geom_raster(
    data = fit_visit_surfs, 
    aes(x = x, y = y, fill = predict.mean)
  ) +
  coord_quickmap() +
  scale_fill_viridis(direction = -1) +
  labs(xlab = "Longitude", ylabs = "Latitude", title = "Aedes Exposure Surface") +
  coord_equal(ratio = 1) +
  theme_bw() +
  theme(panel.border = element_blank(), panel.background = element_blank()) +
  facet_wrap( ~ visit, ncol = 2)
```


```{r simple-exposure-surface, eval = FALSE}
aedes_red <- aedes_red %>% mutate(time = as.numeric(case_when(
  visit == "visit1" ~ 1,
  visit == "visit2" ~ 2,
  visit == "visit3" ~ 3,
  visit == "visit4" ~ 4,
  visit == "visit5" ~ 5
)))

if(params$rerun_simple_surf){
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_red, x = lon, y = lat),
    data = select(aedes_red, log_saliva_elisa, time, wet_season)
  )
  
  simple_surf <- lgm(
    formula = log_saliva_elisa ~ time + wet_season,
    data = spdf,
    grid = 75,
    mc.cores = 9
  )
  
  saveRDS(simple_surf, here("output/map-models", "simple_surf.rds"))
} else {
  simple_surf <- readRDS(here("output/map-models", "simple_surf.rds"))
}

plot(simple_surf$raster$predict.mean, main = "Simple model Aedes Exposure Surface",asp=1)
```


```{r model-exposure-surface, eval = FALSE}
if(params$rerun_model_surf){
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_red, x = lon, y = lat),
    data = select(aedes_red, log_saliva_elisa, 
      gender, 
      age_cented7, distance_to_river_scaled,
      modal_land_type,
      num_toilets_in_home, num_domestic_water_containers_in_home,
      insecticide_spray, larvicide_applied_to_water,
      NFI250_home, EVI250_home,
      wet_season, visit_year,
      visit5
    ))
  
  fit_model_surf <- lgm(
    formula = log_saliva_elisa ~ gender + 
      age_cented7  + distance_to_river_scaled +
      modal_land_type +
      num_toilets_in_home + num_domestic_water_containers_in_home +
      insecticide_spray + larvicide_applied_to_water  +
      NFI250_home + EVI250_home +
      wet_season + visit_year +
      visit5,
    data = spdf,
    grid = 75,
    mc.cores = 9
  )
  
  saveRDS(fit_model_surf, here("output/map-models", "fit_model_surf.rds"))
} else {
  fit_model_surf <- readRDS(here("output/map-models", "fit_model_surf.rds"))
}

plot(fit_model_surf$raster$predict.mean, main = "Model Aedes Exposure Surface",asp=1)
```

```{r wetseason-exposure-surface, eval = FALSE}
aedes_red1 <- filter(aedes_red, wet_season == "yes") 

if(params$rerun_simple_surf){
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_red1, x = lon, y = lat),
    data = select(aedes_red1, log_saliva_elisa)
  )
  
  wet_season_surf <- lgm(
    formula = log_saliva_elisa ~ 1,
    data = spdf,
    grid = 75,
    mc.cores = 9
  )
  
  saveRDS(wet_season_surf, here("output/map-models", "wet_season_surf.rds"))
} else {
  wet_season_surf <- readRDS(here("output/map-models", "wet_season_surf.rds"))
}

plot(wet_season_surf$raster$predict.mean, main = "Wet season Aedes Exposure Surface",asp=1)
```


```{r dryseason-exposure-surface, eval = FALSE}
aedes_red2 <- filter(aedes_red, wet_season == "no") 

if(params$rerun_simple_surf){
  spdf <- SpatialPointsDataFrame(
    coords = select(aedes_red2, x = lon, y = lat),
    data = select(aedes_red2, log_saliva_elisa)
  )
  
  dry_season_surf <- lgm(
    formula = log_saliva_elisa ~ 1,
    data = spdf,
    grid = 75,
    mc.cores = 9
  )
  
  saveRDS(dry_season_surf, here("output/map-models", "dry_season_surf.rds"))
} else {
  dry_season_surf <- readRDS(here("output/map-models", "dry_season_surf.rds"))
}

plot(dry_season_surf$raster$predict.mean, main = "Dry season Aedes Exposure Surface",asp=1)
```


